---
title: "GNG_TUS_Study_1"
author: "nomi"
date: "2023-04-05"
output: html_document
---


#### LOAD LIBRARIES
```{r}
library(pacman)

p_load (tidyverse, BayesFactor, lmerTest, rms, htmltools, bridgesampling, rstanarm,dplyr, magrittr, ggplot, scales, RColorBrewer, parsnip, zoo, tibbletime, wesanderson, stringr, yarr, BiocManager, afex, lmer, GGally, lmerTest, aod, splines, report)

```


```{r}
theme_APA <- theme_bw()+
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          axis.line = element_line(size = 1),                                        
          text = element_text(
              size = 20,
              face="bold"), 
          axis.text = element_text(
              size = 20,
              face="plain",
              colour="black"),
          legend.title = element_blank(),
          legend.position = 'top',
          legend.direction = "horizontal",
          legend.text = element_text(
              face="plain",
              colour="black",
              size=20),
          strip.text.x = element_text(
              size = 20,
              face = "bold"),
          panel.background = element_rect(
              fill='white',
              colour='white'),
          strip.background = element_rect(
              fill='white',
              colour='white'),
          axis.title.x = element_text(
              margin = margin(t = 10)),
          plot.margin = grid::unit(c(5, 5, 5, 5), "mm"),
          plot.caption = element_text(size=15)
          )
```

####insert .txt files
```{r}
sham<- tibble(filename = list.files("1.SHAM", "*.txt", full.names=TRUE)) %>% 
    group_by(filename) %>% 
    do(read.table(.$filename))

ai<- tibble(filename = list.files("2.AI", "*.txt", full.names=TRUE)) %>% 
    group_by(filename) %>% 
    do(read.table(.$filename))

dacc<- tibble(filename = list.files("3.dACC", "*.txt", full.names=TRUE)) %>% 
    group_by(filename) %>% 
    do(read.table(.$filename))

```

####add condition column

```{r}
sham <- sham %>%
      mutate (condition="sham")
ai <- ai %>%
      mutate (condition="ai")
dacc <- dacc %>%
      mutate (condition="dacc")
```

#### Set variable names
```{r}
sham <- sham %>% set_names(c("ID", "stim_ID", "GW", "GAL", "NGW", "NGL", "jitter1", 
              "jitter2", "RT", "outcomefeed", "condition"))

dacc <- dacc %>% set_names(c("ID", "stim_ID", "GW", "GAL", "NGW", "NGL", "jitter1", 
              "jitter2", "RT", "outcomefeed", "condition"))
ai <- ai %>% set_names(c("ID", "stim_ID", "GW", "GAL", "NGW", "NGL", "jitter1", 
              "jitter2", "RT", "outcomefeed", "condition"))
```


####combine datasets
```{r}
tus <-bind_rows(sham, ai, dacc)
```


#### Change name of ID rows to match the subj_ID (i.e.  "pilot data/DBGE0324_log.txt" --> "DBGE0324")
```{r}
tus <- tus %>%
      mutate_at("ID", str_replace, "1.SHAM/", "")# & "log.txt", "")

tus <- tus %>%
      mutate_at("ID", str_replace, "2.AI/", "")

tus <- tus %>%
      mutate_at("ID", str_replace, "3.dACC/", "")

tus <- tus %>%
      mutate_at("ID", str_replace, "_SHAM_2", "_sham")
tus <- tus %>%
      mutate_at("ID", str_replace, "_SHAM_3", "_sham")
tus <- tus %>%
      mutate_at("ID", str_replace, "_SHAM_1", "_sham")
tus <- tus %>%
      mutate_at("ID", str_replace, "_SHAM__1", "_sham")
tus <- tus %>%
      mutate_at("ID", str_replace, "_dACC_2", "_dACC")
tus <- tus %>%
      mutate_at("ID", str_replace, "_dACC_3", "_dACC")
tus <- tus %>%
      mutate_at("ID", str_replace, "_dACC_1", "_dACC")

tus <- tus %>%
      mutate_at("ID", str_replace, "_ACC_2", "_dACC")
tus <- tus %>%
      mutate_at("ID", str_replace, "_ACC_1", "_dACC")


tus <- tus %>%
      mutate_at("ID", str_replace, "_AI_2", "_AI")
tus <- tus %>%
      mutate_at("ID", str_replace, "_AI_3", "_AI")
tus <- tus %>%
      mutate_at("ID", str_replace, "_AI_1", "_AI")

tus <- tus %>%
      mutate_at("ID", str_replace, "_log.txt", "")

tus <- tus %>%
      mutate_at("ID", str_replace, "SINB_0180", "SINB0180")
```


#### Add response col (press - no_press)
```{r}
tus$response <- with(tus, ifelse(RT>0, "press", "no_press"))
tus$GoResponse <- with(tus, ifelse(RT>0, 1, 0)) 
```

### Add Cue column (if stim_ID=NGW then NGW, etc. for  NGL, GW, GAL)
```{r}
tus$Cue <- ifelse(tus$stim_ID == tus$NGL, 'NGL',
                ifelse(tus$stim_ID == tus$NGW, 'NGW', 
                ifelse(tus$stim_ID == tus$GW, 'GW', 
              ifelse(tus$stim_ID == tus$GAL, 'GAL', NA))))
    ```

#### Add GNG col (Go-noGO)
```{r}
tus$req_action <- ifelse(tus$stim_ID == tus$NGL, 'noGo',
                ifelse(tus$stim_ID == tus$NGW, 'noGo', 'Go'))   
#NB's way: 
#pilot$ReqAction <- ifelse(pilot$Cue == 'NGL', 'NoGo',
            #       ifelse(pilot$Cue == 'NGW', 'NoGo',
             #      ifelse(pilot$Cue == 'GW', 'Go',
              #      felse(pilot$Cue == 'GAL', 'Go', NA))))
```
 
#### Add correct column (0-1)  
```{r}
tus <- tus %>%
  mutate(correct = ifelse(req_action == "noGo", ifelse(response == "no_press", 1, 0), 
         
                    ifelse(req_action == "Go", ifelse(response == "press", 1, 0), 1)))
```
        
        
#### Add win_lose column (win - lose) 
```{r}
tus$feedback <- recode_factor(tus$outcomefeed, "-1" = "lose", 
                                "1" = "win", "0"= "neutral")
```
      
### Add Win/Avoid condition column (if stim_ID=NGW then NGW, etc. for  NGL, GW, GAL)
```{r}
tus$OutValence <- ifelse(tus$Cue == 'NGL', 'Avoid',
                   ifelse(tus$Cue == 'NGW', 'Win',
                   ifelse(tus$Cue == 'GW', 'Win',
                   ifelse(tus$Cue == 'GAL', 'Avoid', NA))))
```

#### Add salient feedback column only
```{r}
tus <- tus %>%
  mutate(salient = ifelse(feedback == "win","win",
                      ifelse(feedback == "lose", "lose", NA)));View(tus)

```
        
        
        ###Trial column & block column
```{r}
#1,2,3...100...320
tus <- tus %>%
  group_by(ID) %>%
  mutate(trial_number = row_number());View(tus)

#block 1, 2, 3, 4   =====sos with the trials that have 400 instead of 320
tus$block <- ifelse(tus$trial_number == 1:80, '1',
                ifelse(tus$trial_number == 81:160, '2', 
                ifelse(tus$trial_number == 161:240, '3', 
              ifelse(tus$trial_number == 241:320, '4', NA)))); View(tus)

# counts trials of the same condition within each block
count_trials <- rollify(function(x) sum(last(x) == x), window=80)#turns a function 
#into a rolling version of itself for use inside of a call to dplyr::mutate() ,
# however it works equally as well when called from purrr::map()

tus <- tus %>%
  group_by(ID, block) %>%
  mutate(TrialCount = count_trials(Cue)) %>%
  group_by(ID, block, Cue) %>%
  mutate(TrialCount = ifelse(is.na(TrialCount), row_number(ID), TrialCount))

View(tus)
```

#MEAN RT - PRESSES (distribution of RT)
```{r}
tus_presses <- subset(tus, RT != "0") # exlude 0s (no presses)
RT_presses <-tus_presses%>%  group_by(condition) %>% 
  summarise(Mean_RT = mean(RT, na.rm = TRUE))
RT_presses_many_variables <-tus_presses %>%  group_by(condition, req_action, correct, response) %>% 
  summarise(Mean_RT = mean(RT, na.rm = TRUE))

```

```{r}
# get mean RT per participant
MeanRTpersub <- tus %>% filter(response == "press")%>% group_by(Cue, ID, req_action, OutValence,condition) %>% summarise(RT = mean(RT))
yarrr::pirateplot(formula = RT ~ req_action + OutValence + condition,    # DV = reaction time, IV1 = required action, IV2 = outcome valence
                  data = MeanRTpersub,           
                  theme = 2,
                  main = "Condtion",
                  ylab = "Reaction Time (ms)",
                  ylim = c(400, 1000),
                  bean.f.o = .4, # Bean fill
                  bean.b.o = .2, # Light bean border
                  point.o = .5, # Points (opacity)
                  inf.disp = "line",
                  inf.f.o = 0.8, # Inference fill
                  inf.b.o = 0.8, # Inference border
                  avg.line.o = 0, # Average line
                  point.pch = 21,
                  point.bg = "white",
                  point.cex = .7) + theme_APA



# get mean RT per participant
MeanRTpersub <- tus %>% filter(response == "press")%>% group_by(Cue, ID, req_action, OutValence,condition, correct) %>% summarise(RT = mean(RT))
yarrr::pirateplot(formula = RT ~  OutValence + condition + correct,    
                  data = MeanRTpersub,           
                  theme = 2,
                 # main = "Condition",
                  ylab = "Reaction Time (ms)",
                  ylim = c(300, 1000),
                  bean.f.o = .4, # Bean fill
                  bean.b.o = .2, # Light bean border
                  point.o = .5, # Points (opacity)
                  inf.disp = "line",
                  inf.f.o = 0.8, # Inference fill
                  inf.b.o = 0.8, # Inference border
                  avg.line.o = 0, # Average line
                  point.pch = 21,
                  point.bg = "white",
                  point.cex = .7) 
```

#proportion of GO response per condition -----------need to choose correct responses (320 trials)
```{r}

# compute proportion of go responses for each participant
MeanGoResppersub <- tus %>% group_by(ID, OutValence, Cue, req_action, block, TrialCount) %>% summarise(GoResponse = mean(GoResponse))
# compute mean proportion of go responses 
MeanGoResp <- MeanGoResppersub %>% group_by(Cue, OutValence, req_action, block, TrialCount) %>% summarise(GoResponse = mean(GoResponse))

#plot
ggplot(MeanGoResp) + 
  geom_smooth(aes(TrialCount, GoResponse,colour=OutValence, lty = req_action)) +
  scale_colour_brewer(palette = "Set1") +
  labs(y = "p(GO)", x = "Trial", title = "Trial-by-trial behaviour") 
+ theme_bw() 

#plot Go responses per block
ggplot(MeanGoResp) + 
  geom_smooth(aes(TrialCount,GoResponse,colour=OutValence, lty = req_action)) +
  scale_colour_brewer(palette = "Set1") +
  facet_grid(~block)+
  theme_bw() +
  labs(y = "p(GO)", x = "Trial", title = "Trial-by-trial behaviour") 
```

```{r}
ggplot(tus,
       aes(x=condition, y= correct, color = Cue, fill= Cue)) + 
  geom_bar(stat = "identity")

#presses for noGos 
ggplot(tus,
       aes(x=condition, y= correct, color = condition, fill= condition)) + 
  geom_bar(stat = "identity") +
  facet_grid(~response +req_action)

#errors
ggplot(tus,
       aes(x=condition, y= correct, color = condition, fill= condition)) + 
  geom_bar(stat = "identity") +
  facet_grid(~req_action)



#correct counts per Cue
ccc<-tus %>% group_by (req_action, condition)%>% count (correct);View (ccc)

```

