---
title: "TUS_analysis_behavioral data"
author: "nomi"
date: '2022-09-23'
output: html_document
---

```{r}
#library(usethis)
#git_remotes()
#use_github()
```

      
                ### PREPROCESSING
  
#### LOAD LIBRARIES
```{r}
library(pacman)

p_load(tidyverse, BayesFactor, lmerTest, rms, htmltools, bridgesampling, rstanarm,dplyr, magrittr, ggplot, scales, RColorBrewer, parsnip, zoo, tibbletime, wesanderson, yarr)

```

#### Insert .txt files
```{r}
pilot<- tibble(filename = list.files("pilot data", "*.txt", full.names=TRUE)) %>% 
  group_by(filename) %>% 
  do(read.table(.$filename))

#log <- read.table(file = "MRGI0033_log.txt", header = FALSE)
```



#### Set variable names
```{r}
pilot <- pilot %>% set_names(c("ID", "stim_ID", "GW", "GAL", "NGW", "NGL", "jitter1", 
              "jitter2", "RT", "outcomefeed"))

```


#### Change name of ID rows to match the subj_ID (i.e.  "pilot data/DBGE0324_log.txt" --> "DBGE0324")
```{r}
library(stringr)
pilot <- pilot %>%
      mutate_at("ID", str_replace, "pilot data/", "")# & "log.txt", "")

pilot <- pilot %>%
      mutate_at("ID", str_replace, "_log.txt", "")
```

#### Add response col (press - no_press)
```{r}
pilot$response <- with(pilot, ifelse(RT>0, "press", "no_press"))
pilot$GoResponse <- with(pilot, ifelse(RT>0, 1, 0))
```

### Add Cue column (if stim_ID=NGW then NGW, etc. for  NGL, GW, GAL)
```{r}
pilot$Cue <- ifelse(pilot$stim_ID == pilot$NGL, 'NGL',
                ifelse(pilot$stim_ID == pilot$NGW, 'NGW', 
                ifelse(pilot$stim_ID == pilot$GW, 'GW', 
              ifelse(pilot$stim_ID == pilot$GAL, 'GAL', NA))))
    ```

#### Add GNG col (Go-noGO)
```{r}
pilot$req_action <- ifelse(pilot$stim_ID == pilot$NGL, 'noGo',
                ifelse(pilot$stim_ID == pilot$NGW, 'noGo', 'Go'))   

#NB's way: 
#pilot$ReqAction <- ifelse(pilot$Cue == 'NGL', 'NoGo',
            #       ifelse(pilot$Cue == 'NGW', 'NoGo',
             #      ifelse(pilot$Cue == 'GW', 'Go',
              #      felse(pilot$Cue == 'GAL', 'Go', NA))))
```
 
#### Add correct column (0-1)  
```{r}
pilot <- pilot %>%
  mutate(correct = ifelse(req_action == "noGo", ifelse(response == "no_press", 1, 0), 
         
                    ifelse(req_action == "Go", ifelse(response == "press", 1, 0), 1)))
```
        

#### Add win_lose column (win - lose) 
```{r}
pilot$win_lose_neutral <- recode_factor(pilot$outcomefeed, "-1" = "lose", 
                                "1" = "win", "0"= "neutral")
```
      
### Add Win/Avoid condition column (if stim_ID=NGW then NGW, etc. for  NGL, GW, GAL)
```{r}
pilot$OutValence <- ifelse(pilot$Cue == 'NGL', 'Avoid',
                   ifelse(pilot$Cue == 'NGW', 'Win',
                   ifelse(pilot$Cue == 'GW', 'Win',
                   ifelse(pilot$Cue == 'GAL', 'Avoid', NA))))
```

###Trial column & block column
```{r}
#1,2,3...100...400
pilot <- pilot %>%
  group_by(ID) %>%
  mutate(trial_number = row_number())

#block 1, 2, 3, 4
pilot$block <- ifelse(pilot$trial_number == 1:100, '1',
                ifelse(pilot$trial_number == 101:200, '2', 
                ifelse(pilot$trial_number == 201:300, '3', 
              ifelse(pilot$trial_number == 301:400, '4', NA))))

# counts trials of the same condition within each block
count_trials <- rollify(function(x) sum(last(x) == x), window=100)#turns a function 
#into a rolling version of itself for use inside of a call to dplyr::mutate() ,
# however it works equally as well when called from purrr::map()

pilot <- pilot %>%
  group_by(ID, block) %>%
  mutate(TrialCount = count_trials(Cue)) %>%
  group_by(ID, block, Cue) %>%
  mutate(TrialCount = ifelse(is.na(TrialCount), row_number(ID), TrialCount))

View(pilot)

#pilot$per_20trials <- ifelse(pilot$trial_number == 1:20, 'a.20',
 #               ifelse(pilot$trial_number == 21:40, 'b.40', 
  #              ifelse(pilot$trial_number == 41:60, 'c.60', 
   #           ifelse(pilot$trial_number == 61:80, 'd.80',
    #            ifelse(pilot$trial_number == 81:100, 'e.100',
     #                  ifelse(pilot$trial_number == 101:120, 'a.20',
      #          ifelse(pilot$trial_number == 121:140, 'b.40', 
       #         ifelse(pilot$trial_number == 141:160, 'c.60', 
        #      ifelse(pilot$trial_number == 161:180, 'd.80',
         #       ifelse(pilot$trial_number == 181:200, 'e.100',
          #             ifelse(pilot$trial_number == 201:220, 'a.20',
           #     ifelse(pilot$trial_number == 221:240, 'b.40', 
            #    ifelse(pilot$trial_number == 241:260, 'c.60', 
             # ifelse(pilot$trial_number == 261:280, 'd.80',
              #  ifelse(pilot$trial_number == 281:300, 'e.100',
               #        ifelse(pilot$trial_number == 301:320, 'a.20',
                #ifelse(pilot$trial_number == 321:340, 'b.40', 
                #ifelse(pilot$trial_number == 341:360, 'c.60', 
              #ifelse(pilot$trial_number == 361:380, 'd.80',
               # ifelse(pilot$trial_number == 381:400, 'e.100', NA))))))))))))))))))))
                       
#I want to divide each participants' trials into chunks of 5
          #n_chunks = 80

        #pilot<-pilot %>% 
        #group_by(ID) %>% 
        #mutate(per_5trials = rep(1:n_chunks, 
                       # each = ceiling(n() / n_chunks))[1:n()]) #rep=repeat
#ceiling() is the function that takes two parameters one parameter that is vector with sequence along to divide the vector sequentially and second is chunk length, which represents the length of chunk to be divided



#I want to divide each participants' trials into chunks of 5
          #_chunks = 20

            #pilot<-pilot %>% 
            # group_by(ID) %>% 
            #mutate(per_20trials = rep(1:n_chunks, 
           #each = ceiling(n() / n_chunks))[1:n()])
```


#write .csv file
```{r}
write.csv(x=pilot, "pilot.csv") 
          #How to import:
            #pilot <- read.csv(file = 'pilot.csv')
```


          
          ### PROCESSING - COUNTS AND PLOTS


 #### RTs
 
   ##Distribution of RT for presses
```{r}
 #MEAN RT - PRESSES (distribution of RT)
pilot_presses <- subset(pilot, RT != "0") # exlude 0s (no presses)
RT_presses <-pilot_presses%>%  group_by(RT, ID) %>% 
  summarise(Mean_RT = mean(RT, na.rm = TRUE));RT_presses #%>%
 # filter(CorrectResponse == "Correct")

ggplot(data = RT_presses, 
       aes(x = Mean_RT)) + 
  geom_histogram()+ ggtitle ("Distribution of RT for presses")

# get mean RT per participant
MeanRTpersub <- pilot %>% filter(response == "press")%>% group_by(Cue, ID, req_action, OutValence) %>% summarise(RT = mean(RT))
yarrr::pirateplot(formula = RT ~ req_action + OutValence,    # DV = reaction time, IV1 = required action, IV2 = outcome valence
                  data = MeanRTpersub,           
                  theme = 2,
                  main = "Condtion",
                  ylab = "Reaction Time (ms)",
                  ylim = c(400, 1000),
                  bean.f.o = .4, # Bean fill
                  bean.b.o = .2, # Light bean border
                  point.o = .5, # Points (opacity)
                  inf.disp = "line",
                  inf.f.o = 0.8, # Inference fill
                  inf.b.o = 0.8, # Inference border
                  avg.line.o = 0, # Average line
                  point.pch = 21,
                  point.bg = "white",
                  point.cex = .7)
```

 ##RTs Cue
```{r}
# RTs for each Cue
ggplot(data = MeanRTpersub,
        aes(x = Cue,                                 
            y =  RT)) +                              
   stat_summary(fun = "mean", geom = "point") +        
   stat_summary(fun.data = "mean_se", geom = "errorbar")

# get mean RT per Cue per participant
MeanRTcue <- pilot %>% filter(response == "press")%>% group_by(Cue, ID, req_action, OutValence) %>% summarise(RT = mean(RT))
yarrr::pirateplot(formula = RT ~ Cue,    # DV = reaction time, IV1 = Cue
                  data = MeanRTpersub,           
                  theme = 2,
                  main = "RT per Cue",
                  ylab = "Reaction Time (ms)",
                  ylim = c(350, 1000),
                  bean.f.o = .4, # Bean fill
                  bean.b.o = .2, # Light bean border
                  point.o = .5, # Points (opacity)
                  inf.disp = "line",
                  inf.f.o = 0.8, # Inference fill
                  inf.b.o = 0.8, # Inference border
                  avg.line.o = 0, # Average line
                  point.pch = 21,
                  point.bg = "white",
                  point.cex = .7)
```
 ##RTs Block
```{r}
#Cue per block per RT
ggplot(pilot%>%  
         filter(response != "no_press")%>%
         group_by(Cue),
        aes(x = block,                                 
            y =  RT,                                  
            group = Cue,                                 
            color = Cue)) +                              
     stat_summary(fun = "mean", geom = "point") +        
   stat_summary(fun.data = "mean_se", geom = "errorbar")
####try number of times == press / times cue presented!!!!

# get mean RT per block per participant 
MeanRTcueblock <- pilot %>% filter(response == "press")%>% group_by(block, Cue, ID, req_action, OutValence) %>% summarise(RT = mean(RT))
yarrr::pirateplot(formula = RT ~ block + Cue,    # DV = reaction time, IV1= block, IV2 = Cue
                  data = MeanRTcueblock,           
                  theme = 2,
                  main = "RT cue per block",
                  ylab = "Reaction Time (ms)",
                  ylim = c(350, 1200),
                  bean.f.o = .4, # Bean fill
                  bean.b.o = .2, # Light bean border
                  point.o = .5, # Points (opacity)
                  inf.disp = "line",
                  inf.f.o = 0.8, # Inference fill
                  inf.b.o = 0.8, # Inference border
                  avg.line.o = 0, # Average line
                  point.pch = 21,
                  point.bg = "white",
                  point.cex = .7)
```
#!!!!!!Repeated measures so we need to measure per participant first.

 ##Correct counts per Cue, per ID
```{r}
# compute proportion of correct response for each participant
MeanCorrectpersub <- pilot %>% group_by(ID, Cue,block, req_action, OutValence, TrialCount) %>% summarise(correct = mean(correct))
# compute mean proportion of correct response
MeanCorrect <- MeanCorrectpersub %>% group_by(Cue, block,req_action, OutValence, TrialCount) %>% summarise(correct = mean(correct))
View(MeanCorrect)
# plot
ggplot(MeanCorrect) + 
  geom_smooth(aes(TrialCount,correct*100, colour=req_action, lty = OutValence)) +
  scale_colour_brewer(palette = "Set3") +
  theme_dark() +
  labs(y = "% correct", x = "Trial", title = "Trial-by-trial behaviour")

# plot correct per block
ggplot(MeanCorrect_b) + 
  geom_smooth(aes(TrialCount, correct*100, colour=req_action, lty = OutValence)) +
  #scale_colour_brewer(palette = "Set3") +
  facet_grid(~block)+
  theme_light() +
  labs(y = "% correct", x = "Trial", title = "Trial-by-trial behaviour")

```

  ## proportion of GO response per condition
```{r}
# compute proportion of go responses for each participant
MeanGoResppersub <- pilot %>% group_by(ID, Cue, req_action, OutValence, block, TrialCount) %>% summarise(GoResponse = mean(GoResponse))
# compute mean proportion of go responses 
MeanGoResp <- MeanGoResppersub %>% group_by(Cue, req_action, block, OutValence, TrialCount) %>% summarise(GoResponse = mean(GoResponse))

#plot
ggplot(MeanGoResp) + 
  geom_smooth(aes(TrialCount,GoResponse,colour=req_action, lty = OutValence)) +
  scale_colour_brewer(palette = "Set1") +
  theme_bw() +
  labs(y = "p(GO)", x = "Trial", title = "Trial-by-trial behaviour")

#plot Go responses per block
ggplot(MeanGoResp) + 
  geom_smooth(aes(TrialCount,GoResponse,colour=req_action, lty = OutValence)) +
  scale_colour_brewer(palette = "Set1") +
  facet_grid(~block)+
  theme_bw() +
  labs(y = "p(GO)", x = "Trial", title = "Trial-by-trial behaviour")
```



```{r}
#correct counts per Cue
pilot %>% group_by (Cue)%>% count (correct)


ggplot(pilot,
       aes(x=Cue, y= correct, color = Cue, fill= Cue)) + 
  geom_bar(stat = "identity")

#correct per ID
c<-pilot %>% filter(correct == "1")%>% group_by (ID)%>% count (correct)


mean(c$n) #avg of 307.444 correct responses--> 
          #may be if a person has less than 230 correct responses --> CUT? or below 60? see below aggregate

   

#PROPORTIONs - correct PER PARTCIPANT


#the proportion of 1s by participant, + more i.e. sound, and language.
#Because the proportion of 1s in a vector with only 0s and 1s is just the mean, this should work:

aggregate(data=pilot, correct ~ ID, FUN="mean")

df <- aggregate(data=pilot, correct ~ ID, FUN="mean")
p <- ggplot(df)
p <- p + geom_bar(mapping=aes(x=correct, y=ID), stat='identity')
p + ylab('ID')

#same as above but with stat_summary
ggplot(pilot) + 
  stat_summary(aes(x = ID, y = correct), 
               geom = "bar")


```

# trials playing with correct

```{r}
#Correct per Cue
pilot %>% group_by (Cue)%>% count (correct)


ggplot(pilot, aes(x = Cue, y = response, color = Cue, fill = Cue))+
               geom_bar(stat = "identity")+
  facet_grid(~correct)


#Cue per response (percentage) - NICE one
pilot %>% 
  group_by(correct, trial_number)%>%
  count(Cue) %>% 
  mutate(perc_presses=n/900)-> pilot_1 #

 ggplot(pilot_1, aes(x = Cue, y = perc_presses , color = Cue, fill = Cue)) +
   geom_bar(stat = "identity")+
     scale_y_continuous(labels = scales::percent)+
     facet_grid(~correct)
 
 
 

         #with facets = CANNOT do the % (I WANT ALL RESPONSE 0 AND 1S TO APPEAR)
  pilot %>% group_by(correct, trial_number, Cue)%>% count(Cue)
 
 pilot %>% 
  group_by(Cue, correct, response, trial_number)%>%
  count(Cue) %>% 
  mutate(perc_presses=n/900)-> pilot_1 #
ggplot(pilot_1%>% group_by (Cue), 
       aes(x = trial_number, y = perc_presses, color = Cue, fill = Cue)) +
  #xlim(c(0, 80)) + ylim(c(0, 50)) +
  geom_smooth()+
  facet_grid(response~correct)
```


### Number of presses vs no_presses 
```{r}
pilot%>% group_by (Cue)%>% dplyr::count(response) %>% filter(response == "press")


presses_per_Cue<- pilot%>% group_by (Cue, ID)%>% dplyr::count(response) %>% filter(response == "press")
View (presses_per_Cue) #presses for the noGo responses fluctuate a lot per participant  

presses_per_Cue_block<- pilot%>% group_by (Cue, block)%>% dplyr::count(response) %>% filter(response == "press")
View (presses_per_Cue_block)

 #plot presses per Cue
ggplot(pilot %>% 
   filter(response == "press"), aes(x=Cue, y= response)) + 
  geom_bar(stat = "identity")


# plot press vs no press, per Cue better
ggplot(pilot %>%
         group_by(Cue),
         aes(x=response,
             group = Cue,                                 
            color = Cue, fill = Cue)) + 
          geom_bar(stat = "count")

# press per Cue per block
ggplot(pilot %>%
        filter(response == "press"),
         aes(y = block,
             group = Cue,                                 
            color = Cue, fill = Cue)) + 
     # facet_grid(Cue~paste("cue", Cue), scales="free")
          geom_bar(stat = "count")
```
## Percentages plots per trial per block -- a bit confused about the percentages, still

           #OK  % per Cue per block
```{r}
pilot%>% group_by (Cue)%>% dplyr::count(response) %>% filter(response == "press")



pilot %>% 
  filter(response == "press")%>%
  group_by(block)%>%
  count(Cue) %>% 
  mutate(perc_presses=n/900)-> pilot_1 # I believe this is the correct calculation (about 50% GW ifyou sum up the percentages, the other half no presses)
                   #each Cue 25%, 100 in 400trials, 900 in 3600 trials (3600=9participants)
   #here for 9ppts GW:801 in 3600 = 22.25%

 ggplot(pilot_1, aes(x = Cue, y = perc_presses , color = Cue, fill = Cue)) +
   geom_bar(stat = "identity")+
     scale_y_continuous(labels = scales::percent)+
     facet_grid(~block)
```
   
 #per Cue per block per 20 trials (increments of 20 on every block)
```{r}
t20<-pilot%>% filter(response == "press") %>%group_by(response, per_20trials)%>% count(response) 
sum(t20$n/20) #2015 times appeared / 180





pilot %>% 
  filter(response == "press")%>%
  group_by(block, Cue)%>%
    count(per_20trials) %>% 
  mutate(perc_presses = n / 180) -> pilot_0 #5 chunks of 20trials for 10 participants = 5*10=50 = now i have 9 ppt so wrong logic



ggplot(pilot_0, aes(x = per_20trials, y = perc_presses, color = Cue, fill = Cue)) +
  geom_bar(stat = "identity") +
  facet_grid(Cue~block) +
  scale_y_continuous(labels = scales::percent)



```

                    ##OK, per block of 20 trials but not sure why n/250 and not n/50 works here 
```{r}

pilot %>% 
  filter(response == "press")%>%
  group_by(Cue)%>%
    count(per_20trials) %>% 
  mutate(perc_presses = n / 250) -> pilot_2

                #bar plot Cues in chunk of 20 trials
ggplot(pilot_2, aes(x = per_20trials, y = perc_presses, color = per_20trials, fill = per_20trials)) +
  geom_bar(stat = "identity") +
  facet_grid(~Cue) +
  scale_y_continuous(labels = scales::percent)


                 #%per 5 trials

pilot %>% 
  filter(response == "press")%>%
  group_by(Cue)%>%
    count(per_5trials) %>% 
  mutate(perc_presses = n / 25) -> pilot_10 

ggplot(pilot_10, aes(x = per_5trials, y = perc_presses, color = per_5trials, fill = per_5trials)) +
  geom_bar(stat = "identity") +
  facet_grid(~Cue) +
  scale_y_continuous(labels = scales::percent)

```


              #NK: #percentage presses in 20 trial increments 
              
              !!!!!!!these are the best so far   - #################################################################################################################################################################again percentages are wrong
```{r}

pilot %>% 
  filter(response == "press")%>%
  group_by(Cue)%>%
    count(per_20trials) %>% 
  mutate(perc_presses = n / 180) -> pilot_11 #5 chunks of 20 in 100, in 400 (20), in 3600 (180)

         #with facets
g20<-ggplot(pilot_11%>% group_by (Cue), 
       aes(x = per_20trials, y = perc_presses, color = Cue, fill = Cue)) +
  #xlim(c(0, 80)) + ylim(c(0, 50)) +
  geom_point () +
  geom_line ()+
  facet_grid(~Cue)+
 scale_y_continuous(labels = scales::percent)
g20 + geom_smooth()



#For all trials for all trial_numbers

pilot %>% 
  filter(response == "press")%>%
  group_by(Cue)%>%
    count(trial_number) %>% 
  mutate(perc_presses = n / 900) -> pilot_111 #5 chunks of 20 in 100, in 400 (20), in 3600 (180)

         #with facets
g20<-ggplot(pilot_11%>% group_by (Cue), 
       aes(x = trial_number, y = perc_presses, color = Cue, fill = Cue)) +
  #xlim(c(0, 80)) + ylim(c(0, 50)) +
  #geom_point () +
 # geom_line ()+
  facet_grid(~Cue)+
 scale_y_continuous(labels = scales::percent)
g20 + geom_smooth()
```

```{r}
        #without facets

f<-ggplot(pilot_11%>% group_by (Cue), 
       aes(x = per_20trials, y = perc_presses, color = Cue, fill = Cue)) +
# xlim(c(0, 80)) + ylim(c(0, 70)) +
  #geom_point () +
  #geom_line ()+
  scale_y_continuous(labels = scales::percent)


 f + geom_smooth ()
 
  
 # for all trial numbers
f<-ggplot(pilot_111%>% group_by (Cue), 
       aes(x = trial_number, y = perc_presses, color = Cue, fill = Cue)) +
# xlim(c(0, 80)) + ylim(c(0, 70)) +
  #geom_point () +
  #geom_line ()+
  scale_y_continuous(labels = scales::percent)


 f + geom_smooth ()
```

       !!!!!!!these are the best so far   - #################################################################################################################################################################again percentages are wrong
```{r}
 
              #NK: #percentage presses in 5 trial increments
pilot %>% 
  filter(response == "press")%>%
  group_by(Cue)%>%
    count(per_5trials) %>% 
  mutate(perc_presses = n / 80) -> pilot_10 

         #with facets
g<-ggplot(pilot_4%>% group_by (Cue), 
       aes(x = per_5trials, y = perc_presses, color = Cue, fill = Cue)) +
  xlim(c(0, 80)) + ylim(c(0, 50)) +
  geom_point () +
  geom_line ()+
  facet_grid(~Cue) +
  scale_y_continuous(labels = scales::percent)

g1 <- g + geom_smooth ()

plot(g1)
```

```{r}
        #without facets  - i think the best one so far!!!!!!!!!

gg<-ggplot(pilot_4%>% group_by (Cue), 
       aes(x = per_5trials, y = perc_presses, color = Cue, fill = Cue)) +
  xlim(c(0, 80)) + ylim(c(0, 50)) +
  geom_point () +
  geom_line ()+
  scale_y_continuous(labels = scales::percent)



 gg + geom_smooth ()


#gg1 +                                              # Zoom without cutting values
  #coord_cartesian(ylim = c(0.75, 0.09999999))
```

          #====% wrong===== bar plot + hist per 5 trials (I have created an extra column above "per_5trials"
```{r}

pilot %>% 
  filter(response == "press")%>%
  group_by(Cue)%>%
    count(per_5trials) %>% 
  mutate(perc_presses = n / 18) -> pilot_4

ggplot(pilot_4, aes(x = per_5trials, y = perc_presses, color = per_5trials, fill = per_5trials)) +
  geom_bar(stat = "identity") +
  facet_grid(~Cue) +
  scale_y_continuous(labels = scales::percent)

#something is wrong with the percentages.
ggplot(pilot_4, aes(x = per_5trials)) +   
  facet_grid(~Cue) +
   scale_y_continuous(labels = scales::percent)+
  geom_histogram(aes(y=..density..), colour="black", fill="white", binwidth=5)+
 geom_density(alpha=.2, fill="#FF6666") 


            #histogram for all trials 1-400 per cue in sequence

pilot %>% 
  filter(response == "press")%>%
  group_by(Cue)%>%
    count(trial_number) %>% 
  mutate(perc_presses = n / nrow(pilot)) -> pilot_3

                       #not good at the moment        #close to what we need hist (bindwith = 5 means for every 5 trials)
ggplot(pilot_3, aes(x = trial_number)) +
  facet_grid(~Cue) +
   scale_y_continuous(labels = scales::percent)+
  geom_histogram(aes(y=..density..), colour="black", fill="green", binwidth=5)+
 geom_density(alpha=.2, fill="#FF6666") 
```





###Neutral > win > lose
```{r}
#number of win_lose_neutral instances (valence?)
pilot%>% group_by(win_lose_neutral) %>%dplyr::count(win_lose_neutral) 

 
ggplot(pilot,#%>%
        # group_by(GNG),
       aes(x=win_lose_neutral, y= GNG))+ 
  geom_bar(stat = "identity") #normal for neutral to be more.



#presses vs no_presses per cue valence (win, lose, neutral)
pilot%>% group_by(win_lose_neutral, response) %>%dplyr::count(win_lose_neutral) 

ggplot(pilot,
       aes(x=win_lose_neutral,
           color = response, fill = response))+ 
  geom_bar(stat = "count")
```

###Presses per correctness and blocks and response (press vs no_press)
```{r}
#presses per correct and blocks--> they are doing good so far. they learn fast
pilot%>% group_by(correct, response) %>%dplyr::count(correct) 
pilot%>% group_by(correct, block) %>%dplyr::count(correct) # 1st block OK, 2nd block better, 3rd block tired, 4th block better

#How good per block and per response (press vs no_press)
ggplot(pilot,
        aes(x = response,                                 
            y =  correct,                                
            group = block,                                 
           color = block)) +                              
   stat_summary(fun = "mean", geom = "point") +        
   stat_summary(fun = "mean", geom = "line") +         
   stat_summary(fun.data = "mean_se", geom = "errorbar")

#How good per block
ggplot(pilot,
        aes(x = block,                                 
            y =  correct,                                
            group = block,                                 
           color = block)) +                              
   stat_summary(fun = "mean", geom = "point") +        
   stat_summary(fun = "mean", geom = "line") +        
   stat_summary(fun.data = "mean_se", geom = "errorbar")

```
