---
title: "GNG_processing_beha_data"
author: "nomi"
date: "2023-02-20"
output: html_document
---

#### LOAD LIBRARIES
```{r}
library(pacman)

p_load (tidyverse, BayesFactor, lmerTest, rms, htmltools, bridgesampling, rstanarm,dplyr, magrittr, ggplot2, scales, RColorBrewer, parsnip, zoo, tibbletime, wesanderson, stringr, yarr, BiocManager, afex, lmer, GGally, lmerTest, aod, splines, report)

```

```{r}
theme_APA <- theme_bw()+
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          axis.line = element_line(size = 1),                                        
          text = element_text(
              size = 16,
              face="bold"), 
          axis.text = element_text(
              size = 16,
              face="plain",
              colour="black"),
          legend.title = element_blank(),
          legend.position = 'top',
          legend.direction = "horizontal",
          legend.text = element_text(
              face="plain",
              colour="black",
              size=16),
          strip.text.x = element_text(
              size = 16,
              face = "bold"),
          panel.background = element_rect(
              fill='white',
              colour='white'),
          strip.background = element_rect(
              fill='white',
              colour='white'),
          axis.title.x = element_text(
              margin = margin(t = 10)),
          plot.margin = grid::unit(c(5, 5, 5, 5), "mm"),
          plot.caption = element_text(size=8)
          )
```

```{r}
pilot <- read.csv(file = 'pilot.csv')
pilot_dropped <- read.csv(file = 'df.csv') #dropped NAs
```

  
  ### PROCESSING - COUNTS AND PLOTS


      *****RTs
 
#Distribution of RT for presses
```{r}
 #MEAN RT - PRESSES (distribution of RT)
pilot_presses <- subset(pilot, RT != "0") # exlude 0s (no presses)
RT_presses <-pilot_presses%>%  group_by(RT, ID) %>% 
  summarise(Mean_RT = mean(RT, na.rm = TRUE));RT_presses #%>%
 # filter(CorrectResponse == "Correct")

ggplot(data = RT_presses, 
       aes(x = Mean_RT)) + 
  geom_histogram()+ ggtitle ("Distribution of RT for presses") +theme_APA

# get mean RT per participant
MeanRTpersub <- pilot %>% filter(response == "press")%>% group_by(Cue, ID, req_action, OutValence) %>% summarise(RT = mean(RT))
yarrr::pirateplot(formula = RT ~ req_action + OutValence,    # DV = reaction time, IV1 = required action, IV2 = outcome valence
                  data = MeanRTpersub,           
                  theme = 2,
                  main = "Condtion",
                  ylab = "Reaction Time (ms)",
                  ylim = c(400, 1000),
                  bean.f.o = .4, # Bean fill
                  bean.b.o = .2, # Light bean border
                  point.o = .5, # Points (opacity)
                  inf.disp = "line",
                  inf.f.o = 0.8, # Inference fill
                  inf.b.o = 0.8, # Inference border
                  avg.line.o = 0, # Average line
                  point.pch = 21,
                  point.bg = "white",
                  point.cex = .7) + theme_APA
```

#RTs Cue
```{r}
# RTs for each Cue
ggplot(data = MeanRTpersub,
        aes(x = Cue,                                 
            y =  RT)) +                              
   stat_summary(fun = "mean", geom = "point") +        
   stat_summary(fun.data = "mean_se", geom = "errorbar")

# get mean RT per Cue per participant
MeanRTcue <- pilot %>% filter(response == "press")%>% group_by(Cue, ID, req_action, OutValence) %>% summarise(RT = mean(RT))
yarrr::pirateplot(formula = RT ~ Cue,    # DV = reaction time, IV1 = Cue
                  data = MeanRTpersub,           
                  theme = 2,
                  main = "RT per Cue",
                  ylab = "Reaction Time (ms)",
                  ylim = c(450, 1000),
                  bean.f.o = .4, # Bean fill
                  bean.b.o = .2, # Light bean border
                  point.o = .5, # Points (opacity)
                  inf.disp = "line",
                  inf.f.o = 0.8, # Inference fill
                  inf.b.o = 0.8, # Inference border
                  avg.line.o = 0, # Average line
                  point.pch = 21,
                  point.bg = "white",
                  point.cex = .7)
```

#RTs Block
```{r}
#Cue per block per RT
ggplot(pilot%>%  
         filter(response != "no_press")%>%
         group_by(Cue),
        aes(x = block,                                 
            y =  RT,                                  
            group = Cue,                                 
            color = Cue)) + 
          facet_grid (~Cue)+
     stat_summary(fun = "mean", geom = "point") +        
   stat_summary(fun.data = "mean_se", geom = "errorbar")
####try number of times == press / times cue presented!!!!

# get mean RT per block per participant 
MeanRTcueblock <- pilot %>% filter(response == "press")%>% group_by(block, Cue, ID, req_action, OutValence) %>% summarise(RT = mean(RT))
yarrr::pirateplot(formula = RT ~ block + Cue,    # DV = reaction time, IV1= block, IV2 = Cue
                  data = MeanRTcueblock,           
                  theme = 2,
                  main = "RT cue per block",
                  ylab = "Reaction Time (ms)",
                  ylim = c(350, 1200),
                  bean.f.o = .4, # Bean fill
                  bean.b.o = .2, # Light bean border
                  point.o = .5, # Points (opacity)
                  inf.disp = "line",
                  inf.f.o = 0.8, # Inference fill
                  inf.b.o = 0.8, # Inference border
                  avg.line.o = 0, # Average line
                  point.pch = 21,
                  point.bg = "white",
                  point.cex = .7)
```

          ***
             #!!!!!!Repeated measures so we need to measure per participant first
          ***

#Correct counts per Cue, per ID
```{r}
# compute proportion of correct response for each participant
MeanCorrectpersub <- pilot %>% group_by(ID, Cue,block, req_action, OutValence, TrialCount) %>% summarise(correct = mean(correct))
# compute mean proportion of correct response
MeanCorrect <- MeanCorrectpersub %>% group_by(Cue, block,req_action, OutValence, TrialCount) %>% summarise(correct = mean(correct))
View(MeanCorrect)
# plot
ggplot(MeanCorrect) + 
  geom_smooth(aes(TrialCount,correct*100, colour=req_action, lty = OutValence)) +
  scale_colour_brewer(palette = "Set3") +
  theme_dark() +
  labs(y = "% correct", x = "Trial", title = "Trial-by-trial behaviour")

# plot correct per block
ggplot(MeanCorrect) + 
  geom_smooth(aes(TrialCount, correct*100, colour=req_action, lty = OutValence)) +
  #scale_colour_brewer(palette = "Set3") +
  facet_grid(~block)+
  theme_light() +
  labs(y = "% correct", x = "Trial", title = "Trial-by-trial behaviour")

```

#proportion of GO response per condition
```{r}
# compute proportion of go responses for each participant
MeanGoResppersub <- pilot %>% group_by(ID, Cue, req_action, OutValence, block, TrialCount) %>% summarise(GoResponse = mean(GoResponse))
# compute mean proportion of go responses 
MeanGoResp <- MeanGoResppersub %>% group_by(Cue, req_action, block, OutValence, TrialCount) %>% summarise(GoResponse = mean(GoResponse))

#plot
ggplot(MeanGoResp) + 
  geom_smooth(aes(TrialCount,GoResponse,colour=req_action, lty = OutValence)) +
  scale_colour_brewer(palette = "Set1") +
  theme_bw() +
  labs(y = "p(GO)", x = "Trial", title = "Trial-by-trial behaviour") +theme_APA

#plot Go responses per block
ggplot(MeanGoResp) + 
  geom_smooth(aes(TrialCount,GoResponse,colour=req_action, lty = OutValence)) +
  scale_colour_brewer(palette = "Set1") +
  facet_grid(~block)+
  theme_bw() +
  labs(y = "p(GO)", x = "Trial", title = "Trial-by-trial behaviour") +theme_APA
```



```{r}

ggplot(pilot,
       aes(x=Cue, y= correct, color = Cue, fill= Cue)) + 
  geom_bar(stat = "identity")

#correct counts per Cue
ccc<-pilot %>% group_by (Cue)%>% count (correct);View (ccc)

#correct counts per Cue per ID
ccc_id<-pilot %>% group_by (Cue, ID)%>% count (correct);View (ccc_id)

#correct per ID
c<-pilot %>% filter(correct == "1")%>% group_by (ID)%>% count (correct);c

#response per ID
response_per_ppt <-pilot %>% group_by (ID)%>% count (response);View (response_per_ppt)

mean(c$n) #avg of 294 correct responses--> 
          #may be if a person has less than 230 or 210? correct responses --> CUT? or below 53? see below aggregate

   

#PROPORTIONs - correct PER PARTCIPANT


#the proportion of 1s by participant, + more i.e. sound, and language.
#Because the proportion of 1s in a vector with only 0s and 1s is just the mean, this should work:

aggregate(data=pilot, correct ~ ID, FUN="mean") #fun = mean #https://r-coder.com/aggregate-r/

df <- aggregate(data=pilot, correct ~ ID, FUN="mean")
p <- ggplot(df)
p <- p + geom_bar(mapping=aes(x=correct, y=ID), stat='identity')+
  geom_vline(xintercept = 0.53, col = "red")+ 
  geom_vline(xintercept = 0.50, col = "grey")+
   geom_vline(xintercept = 0.80, col = "green")+
  geom_text(aes(x=0.54, label="53%", y=4), colour="black", angle=90) +
geom_text(aes(x=0.49, label="50%", y=9), colour="black", angle=90)+
  geom_text(aes(x=0.79, label="80%", y=6), colour="black", angle=90) 
p + ylab('ID')

#same as above but with stat_summary
ggplot(pilot) + 
  stat_summary(aes(x = ID, y = correct), 
               geom = "bar")
```

# trials playing with correct
```{r}
#Correct per Cue
pilot %>% group_by (Cue)%>% count (correct)


ggplot(pilot, aes(x = Cue, y = response, color = Cue, fill = Cue))+
               geom_bar(stat = "identity")+
  facet_grid(~correct)


#Cue per response (percentage) - NICE one
pilot %>% 
  group_by(correct, trial_number)%>%
  count(Cue) %>% 
  mutate(perc_presses=n/900)-> pilot_1 #

 ggplot(pilot_1, aes(x = Cue, y = perc_presses , color = Cue, fill = Cue)) +
   geom_bar(stat = "identity")+
     scale_y_continuous(labels = scales::percent)+
     facet_grid(~correct)
 
 
                    ***not correct ???@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
      
  MeanCorrectpersub <- pilot %>% group_by(trial_number, ID, Cue,block, req_action, OutValence, TrialCount) %>% summarise(correct = mean(correct))
# compute mean proportion of correct response
MeanCorrect <- MeanCorrectpersub %>% group_by(Cue,trial_number, block,req_action, OutValence, TrialCount) %>% summarise(correct = mean(correct))
# plot @@@@@@@@@Is that all the trials indeed? all not repeated
ggplot(MeanCorrect) + 
  geom_smooth(aes(trial_number,correct*100, colour=req_action, lty = OutValence)) +
  scale_colour_brewer(palette = "Set3") +
  theme_dark() +
  labs(y = "% correct", x = "Trial", title = "Trial-by-trial behaviour")


# plot correct per block --not good
ggplot(MeanCorrect) + 
  geom_smooth(aes(trial_number, correct*100, colour=req_action, lty = OutValence)) +
  #scale_colour_brewer(palette = "Set3") +
  facet_grid(~block)+
  theme_light() +
  labs(y = "% correct", x = "Trial", title = "Trial-by-trial behaviour")

  
  # plot correct per block - not bad
ggplot(MeanCorrect) + 
  geom_smooth(aes(TrialCount, correct*100, colour=req_action, lty = OutValence)) +
  #scale_colour_brewer(palette = "Set3") +
  facet_grid(~block)+
  theme_light() +
  labs(y = "% correct", x = "Trial", title = "Trial-by-trial behaviour")

  
  
  
          ***wrong***
            @@@@@@@@@do per participant first like above nadeige
  
    #with facets = CANNOT do the % (I WANT ALL RESPONSE 0 AND 1S TO APPEAR)
 pilot_1 <- pilot %>% group_by(ID, correct, trial_number, response, Cue)%>% count(Cue)
 
 ggplot(pilot_1%>% group_by (Cue), 
       aes(x = trial_number, y = Cue, color = Cue, fill = Cue)) +
  #xlim(c(0, 80)) + ylim(c(0, 50)) +
  geom_smooth()+
  facet_grid(response~correct)
```


# Number of presses vs no_presses 
```{r}
pilot%>% group_by (Cue)%>% dplyr::count(response) %>% filter(response == "press")


presses_per_Cue<- pilot%>% group_by (Cue, ID)%>% dplyr::count(response) %>% filter(response == "press")
View (presses_per_Cue) #presses for the noGo responses fluctuate a lot per participant  

presses_per_Cue_block<- pilot%>% group_by (Cue, block)%>% dplyr::count(response) %>% filter(response == "press")
View (presses_per_Cue_block)

 #plot presses per Cue
ggplot(pilot %>% 
   filter(response == "press"), aes(x=Cue, y= response, color = Cue, fill = Cue)) + 
  geom_bar(stat = "identity") + theme_APA

 #plot presses per Cue
ggplot(pilot %>% 
   filter(response == "press"), aes(x=req_action, y= response, color = req_action, fill = req_action)) + 
  geom_bar(stat = "identity") + theme_APA

# plot press vs no press, per Cue better
ggplot(pilot %>%
         group_by(Cue),
         aes(x=response,
             group = Cue,                                 
            color = Cue, fill = Cue)) + 
          geom_bar(stat = "count") +theme_APA

# press per Cue per block
ggplot(pilot %>%
        filter(response == "press"),
         aes(y = block,
             group = Cue,                                 
            color = Cue, fill = Cue)) + 
     # facet_grid(Cue~paste("cue", Cue), scales="free")
          geom_bar(stat = "count") + theme_APA
```



#Neutral > win > lose - feedback
```{r}
#number of feedback instances (valence?)
pilot%>% group_by(feedback) %>%dplyr::count(feedback) 

 
ggplot(pilot,#%>%
        # group_by(GNG),
       aes(x=feedback, y= req_action))+ 
  geom_bar(stat = "identity") #normal for neutral to be more.



#presses vs no_presses per cue feedback (win, lose, neutral) ***better***
pilot%>% group_by(feedback, response) %>%dplyr::count(feedback) 

ggplot(pilot,
       aes(x=feedback,
           color = response, fill = response))+ 
  geom_bar(stat = "count")
```

#Presses per correctness and blocks and response (press vs no_press)
```{r}
#presses per correct and blocks--> they are doing good so far. they learn fast
pilot%>% group_by(correct, response) %>%dplyr::count(correct) 
pilot%>% group_by(correct, block) %>%dplyr::count(correct) # 1st block OK, 2nd block better, 3rd block tired, 4th block better

#How good per block and per response (press vs no_press)
ggplot(pilot,
        aes(x = response,                                 
            y =  correct,                                
            group = block,                                 
           color = block)) +                              
   stat_summary(fun = "mean", geom = "point") +        
   stat_summary(fun = "mean", geom = "line") +         
   stat_summary(fun.data = "mean_se", geom = "errorbar")

#How good per block
ggplot(pilot,
        aes(x = block,                                 
            y =  correct,                                
            group = block,                                 
           color = block)) +                              
   stat_summary(fun = "mean", geom = "point") +        
   stat_summary(fun = "mean", geom = "line") +        
   stat_summary(fun.data = "mean_se", geom = "errorbar")

```

