---
title: "rolling_mean_GNG"
author: "nomi"
date: '2022-10-25'
output: html_document
---


#Load data and packages
```{r}
library(pacman)
p_load(tidyverse, BayesFactor, lmerTest, rms, htmltools, bridgesampling, rstanarm,dplyr, magrittr, ggplot(), scales, RColorBrewer, parsnip, zoo, reshape)


pilot <- read.csv(file = 'pilot.csv')

```


      ### V.1
      
  


  ###Rolling average calculations for smoothing "per_5trials" column (=THAT IS PROPORTIONALLY PER 100 TRIALS)
        (not sur if correct)

```{r}
pilot_1<-pilot%>%  
  filter(response == "press")%>%
  group_by (response, Cue, block)%>% dplyr::count(per_5trials) 
```


          #multiple ks
```{r}


rm<-pilot_1 %>%
  group_by(Cue) %>%
  mutate(moving_avg5 = rollmean(n, k=5, fill=NA, align='right'),
        moving_avg10 = rollmean(n, k=10, fill=NA, align='right'),
        moving_avg15 = rollmean(n, k=15, fill=NA, align='right'),
         moving_avg20 = rollmean(n, k=20, fill=NA, align='right'),
         moving_avg25 = rollmean(n, k=25, fill=NA, align='right'),
        moving_avg40 = rollmean(n, k=40, fill=NA, align='right'),
        moving_avg60 = rollmean(n, k=60, fill=NA, align='right'),
        moving_avg90 = rollmean(n, k=90, fill=NA, align='right')) %>% 
         dplyr::ungroup()

            #long format
rm_long<-rm %>% 
  tidyr::pivot_longer(names_to = "rolling_mean_key", 
                    values_to = "rolling_mean_value", 
                    cols = c( 
                             moving_avg5, 
                             moving_avg10,
                             moving_avg15,
                             moving_avg20,
                             moving_avg25,
                             moving_avg40,
                             moving_avg60,
                             moving_avg90))

            #plot
  rm_long%>% 
    ggplot (aes(y = rolling_mean_value, 
                      x = per_5trials, 
                      color = Cue)) + 
                        geom_smooth()
```



            #one k
```{r}
  rm1<-pilot_1 %>%
group_by(Cue) %>%
 mutate(moving_avg5 = rollmean(n, k=5, fill=NA, align='right'))
             #long format
  rm_long1<-rm1 %>% 
  tidyr::pivot_longer(names_to = "rolling_mean_key", 
                    values_to = "rolling_mean_value", 
                    cols = moving_avg5)

            #plot
  rm_long1%>% 
    ggplot (aes(y = rolling_mean_value, 
                      x = per_5trials, 
                      color = Cue)) + 
                        geom_smooth()
  
  ##? HOW TO DO IT WITH PERCENTAGES?

```



 ###### V.2

---
title: "tim_rollingmeans_TUS_beha"
author: "nomi" --added bits
date: '2022-10-25'
output: html_document
---



PRE-PROCESSING FOR CALCULATING ROLLING AVERAGES OF PRESS RESPONSES ACROSS ALL 100 TRIALS FOR EACH CUE, AND PLOTTING:

Creating data frames from Pilot DF that represent all responses from all participants. 

Controlling for Jitter to calculate order of cue presentation: by adding a vector from 1:25 we create an order of presentation (i.e. 1 represents the first time that cue was presented in that block, rather than using trial number which will differ from person to person due to jitter).

Count of 'Press' responses: number of press responses for each cue across all participants and in order of presentation is then calculated.

Roll Mean: a rolling average can then be calculated from the data frames containing all press responses for all participants.

Data frame for plotting: all rolling average calculations are then added to a data frame, converted to long format with 'melt' function and plotted.


#vector representing order cue is presented
```{r}
#This will be used for all Cue DFs
#Make a vec representing order cue is presented, enough so that each cue for each participant has 1:25 of order

Stim_Seq<-c(1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25,1:25)
#vector of 40 sequences.why 40???????

#+++NK: CHANGED TO THIS
Stim_Seq<-c(rep(1:25, 36))#900 OBSERBATIONS FIND CODE SO THIS WILL NOT BE HAPPENING MANUALLY


```



```{r}
#GW
#Create data frame for each Cue for press responses
GW_All_Present<-pilot %>% filter(Cue == "GW")
View(GW_All_Present)

#Add vec
GW_All_Present$Stim_Sequence<-Stim_Seq

#Make response a factor to use .drop = FALSE to keep zeroes in the count
GW_All_Present$response<-as.factor(GW_All_Present$response)

#Count number of presses for all participants across all blocks in order from 1 to 100 (Total amount the cue was presented)
GW_All_Present_Count<- GW_All_Present%>% group_by (Cue, block, Stim_Sequence)%>% dplyr::count(response,.drop = FALSE) %>% filter(response == "press")
as.numeric(GW_All_Present_Count$n)
#Making a DF for just the count col (For some reason the roll mean isnt working with whole DF)
#Count DF
GW_n<-GW_All_Present_Count$n

#As DF
GW_n<-as.data.frame(GW_n)
#Roll mean
GW_n_DF<-GW_n %>%
  mutate(Roll_Mean_21 = zoo::rollmean(GW_n, k=21, fill=NA,align='center'))
```


```{r}
#NGW
#Create data frame for each Cue
NGW_All_Present<-pilot %>% filter(Cue == "NGW")
#Add vec
NGW_All_Present$Stim_Sequence<-Stim_Seq
#Make response a factor to use .drop = FALSE to keep zeroes in the count
NGW_All_Present$response<-as.factor(NGW_All_Present$response)
#Count
NGW_All_Present_Count<- NGW_All_Present%>% group_by (Cue, block, Stim_Sequence)%>% dplyr::count(response,.drop = FALSE) %>% filter(response == "press")
#Count DF
NGW_n<-NGW_All_Present_Count$n

#As DF
NGW_n<-as.data.frame(NGW_n)
#Roll mean
NGW_n_DF<-NGW_n %>%
  mutate(Roll_Mean_21 = zoo::rollmean(NGW_n, k=21, fill=NA,align='center'))
```


```{r}
#NGL
#Create data frame for each Cue
NGL_All_Present<-pilot %>% filter(Cue == "NGL")
#Add vec
NGL_All_Present$Stim_Sequence<-Stim_Seq
#Make response a factor to use .drop = FALSE to keep zeroes in the count
NGL_All_Present$response<-as.factor(NGL_All_Present$response)
#Count
NGL_All_Present_Count<- NGL_All_Present%>% group_by (block, Stim_Sequence)%>% dplyr::count(response,.drop = FALSE) %>% filter(response == "press")

#Count DF
NGL_n<-NGL_All_Present_Count$n

#As DF
NGL_n<-as.data.frame(NGL_n)
#Roll mean
NGL_n_DF<-NGL_n %>%
  mutate(Roll_Mean_21 = zoo::rollmean(NGL_n, k=21, fill=NA,align='center'))
```


```{r}
#GAL
#Create data frame for each Cue
GAL_All_Present<-pilot %>% filter(Cue == "GAL")
#Add vec
GAL_All_Present$Stim_Sequence<-Stim_Seq
#Make response a factor to use .drop = FALSE to keep zeroes in the count
GAL_All_Present$response<-as.factor(GAL_All_Present$response)
#Count
GAL_All_Present_Count<- GAL_All_Present%>% group_by (Cue, block, Stim_Sequence)%>% dplyr::count(response,.drop = FALSE) %>% filter(response == "press")
#As.df
as.data.frame(GAL_All_Present_Count)
#Count DF
GAL_n<-GAL_All_Present_Count$n

#As DF
GAL_n<-as.data.frame(GAL_n)
#Roll mean
GAL_n_DF<-GAL_n %>%
  mutate(Roll_Mean_21 = zoo::rollmean(GAL_n, k=21, fill=NA,align='center'))
```


#Join cols from Rolling Mean DFs

```{r}
#Joining columns to form data frame:
Roll_All_21 <- cbind(GW_n_DF$Roll_Mean_21,GAL_n_DF$Roll_Mean_21,NGW_n_DF$Roll_Mean_21,NGL_n_DF$Roll_Mean_21)

#Making it a data.frame
Roll_All_21<-as.data.frame(Roll_All_21)

#Rename columns
Roll_All_21<-Roll_All_21 %>% 
  rename(
    GW = V1,
    GAL = V2,
    NGW = V3,
    NGL = V4,)

#Add sequence vector
Roll_vec<-1:100

Roll_All_21$Sequence<-Roll_vec

###############
#Plotting the Roll Mean 21 data:

#Long format
Roll_All_21_Long = melt(Roll_All_21, id.vars = c("Sequence"),
                measure.vars = c("GW", "GAL", "NGL", "NGW"))
#Remove NA
Roll_All_21_Long<-na.omit(Roll_All_21_Long)
```

#Roll Mean Plot
```{r}
#Create a custom color scale
#library(RColorBrewer)
myColors <- brewer.pal(4,"Set1")
names(myColors) <- levels(Roll_All_21_Long$variable)
colScale <- scale_colour_manual(name = "variable",values = myColors)

#Roll mean plot
Roll_All_21 <- ggplot(Roll_All_21_Long,aes(Sequence,value,colour = variable, group = variable)) + geom_point() + geom_line()
Roll_All_21_Plot <- Roll_All_21 + colScale

plot(Roll_All_21_Plot)




Roll_All_21 <- ggplot(Roll_All_21_Long,aes(Sequence,value,colour = variable, group = variable))+
  geom_smooth()
Roll_All_21_Plot <- Roll_All_21 + colScale

plot(Roll_All_21_Plot)
```



