---
title: "GNG_TUS_Study_1_320trials_preprocessing"
author: "nomi"
date: "2023-10-31"
output: html_document
---

 

# LOAD LIBRARIES
```{r}
#library(Rccp)
#library(rlang)
library(tibbletime)
library(purrr)
library(stringr)
library(report)
#library(ggplot)
library(ggplot2)
library(dplyr)
#library(lmer)
library(tidyverse)
library(patchwork)
library(ggpubr)
library(jtools) #for explanation of lmer
library(yarr)
library (yarrr)
library(afex)
#install.packages("devtools")
#devtools::install_github("mikabr/ggpirate")
#library(ggpirate)
#p_load ( rms, htmltools, bridgesampling, rstanarm, magrittr, scales, RColorBrewer, 
# parsnip, zoo, wesanderson, yarr, BiocManager, afex, GGally, lmerTest, aod, splines)
```



    #PREPROCESSING

## insert .txt files
```{r}
pilot<- tibble(filename = list.files("pilot_data", "*.txt", full.names=TRUE)) %>% 
    group_by(filename) %>% 
    do(read.table(.$filename))

test_jitters<- tibble(filename = list.files("test_jitters", "*.txt", full.names=TRUE)) %>% 
    group_by(filename) %>% 
    do(read.table(.$filename))

test_rt_jitter_nomi<- tibble(filename = list.files("test_rt_jitter_nomi", "*.txt", full.names=TRUE)) %>% 
    group_by(filename) %>% 
    do(read.table(.$filename))
```

```

## Set variable names
```{r}
pilot <- pilot %>% set_names(c("ID", "stim_ID", "GW", "GAL", "NGW", "NGL", "jitter1", 
              "jitter2", "RT", "outcomefeed"))


test_jitters <- test_jitters %>% set_names(c("ID", "jitter1", 
              "jitter2", "stim_ID", "GW", "GAL", "NGW", "NGL",  "break", "block"))
   
   test_rt_jitter_nomi <- test_rt_jitter_nomi %>% set_names(c("ID", "stim_ID", "GW", "GAL", "NGW", "NGL", "jitter1", 
              "jitter2", "RT", "outcomefeed"))           
              
```


#
 ##write.csv
```{r}
write.csv(pilot, "pilot.csv")

write.csv(test_jitters, "test_jitters.csv")

write.csv(test_rt_jitter_nomi, "test_rt_jitter_nomi.csv")


```



