---
title: "cumulative_reward_analysis"
author: "Nadège B."
date: "2024-07-31"
output:
  html_document: default
---

#Load libraries and custom functions
```{r include=FALSE}
library(ggplot2)
library (yarrr)
library(tidyverse)
library(forcats)
library(lmerTest)
library(effects)
library(sjPlot)
library(emmeans)
library(sommer)
library(here) # find your project's files, based on the current working directory at the time when the package is loaded

# load custom function
source(here("custom_functions_lme4.R"))
```

# READ FILES
```{r include=FALSE}
tus <- read_csv("GNG_TUS_S1.csv")
tus_filtered <- read_csv ("GNG_tus_filtered_S1.csv")
```

# Compute cumulative reward/outcome column - this is computed independently for each cue
```{r}
tus_filtered <- tus_filtered %>%
  group_by(ID, condition, Cue, block) %>%
  arrange(trial_number, .by_group = TRUE) %>%
  mutate(cumulative_reward = cumsum(outcomefeed)) %>%
  ungroup()  # Ungroup to return to regular data frame

# check whether there are missing values
filtered <- tus_filtered %>%
  filter(is.na(cumulative_reward))
```

# Summarize by condition
```{r}
cumul_reward <- tus_filtered %>%
  group_by(ID, condition, req_action, OutValence, Cue, TrialCount) %>%
  summarise(
    cumrew_mean = mean(cumulative_reward, na.rm = TRUE),
    cumrew_sd = sd(RT, na.rm = TRUE),
    n = n()  # Count the number of observations for each condition
  )
```

# create a nice plot
```{r}
ggplot(data = cumul_reward, 
  mapping = aes(x = TrialCount, y = cumrew_mean, color = forcats::fct_rev(condition), fill = forcats::fct_rev(condition) )) + 
  stat_summary(fun = mean, geom = "point") + # mean accuracy across participants in each trial
  stat_summary(fun = mean, geom = "line") +  # connect the means with a line
  geom_smooth(method = "loess", se = TRUE, linewidth = 1.2, alpha = 0.2) +  # Smooth curve with standard error
  scale_x_continuous(name = 'Trial'   , breaks = 1:20, labels = function(x) ifelse(x%%2==0, x, '')) + 
  scale_y_continuous(name = 'Cumulative Outcome', breaks = scales::pretty_breaks()) +
  facet_grid(forcats::fct_relevel(OutValence, "Win", "Avoid") ~ req_action, scales = "free") +                # split by domain and by symbol condition
  scale_color_brewer(palette = "Set2", name = "Condition") +  # Use a qualitative color palette
  scale_fill_brewer(palette = "Set2", name = "Condition") +  # Use a qualitative color palette
  theme_bw()
```

# GLM analyses

```{r}
# convert variables to factors
tus_filtered <- tus_filtered %>% mutate_at(c('req_action', 'OutValence', 'condition', 'ID'), as.factor)
# refactor reference level
tus_filtered <- within(tus_filtered, req_action <- relevel(req_action, ref = "noGo"))
tus_filtered <- within(tus_filtered, OutValence <- relevel(OutValence, ref = "Win"))
tus_filtered <- within(tus_filtered, condition <- relevel(condition, ref = "Sham"))
```

GLM -seperate analyses on win and avoid conditions, to avoid triple interactions (difficult to interpret) and
as comparing the two is not the main focus of interest of the study.

## Win condition
```{r}
tus_win <- tus_filtered %>% filter(OutValence == "Win")
# testing full model
mcumwin_full <- lmer(cumulative_reward ~ req_action*condition + (req_action*condition | ID), data  = tus_win)
summary(mcumwin_full)
```

### check for singularity and effect of random slopes
```{r}
# check for singularity
isSingular(mcumwin_full)

# Diagnosis with RePsychLing approach: PCA on random effects variance-covariance estimates
rePCA_full <- rePCA(mcumwin_full)
summary(rePCA_full$ID)
```

The random slopes for the interaction terms have very little impact on the model, therefore we'll remove them

### model reduced to random slopes with substantial proportion of variance explained
```{r}
mcumwin <- lmer(cumulative_reward ~ req_action*condition + (req_action + condition | ID), data  = tus_win)
summary(mcumwin)
tab_model(mcumwin)
```

```{r}
plot(allEffects(mcumwin), ask=FALSE)
```

### display simple effects for each condition
```{r}
emmeans(mcumwin, pairwise ~ condition | req_action)

```

### plot effects 
```{r}
Labels = c("Intercept", "Required Action", "Stimulation AI", "Stimulation dACC", "Req. Action x AI", "Req. Action x dACC")
pwin <- custom_coefplot(mcumwin, yLabels = Labels,
                      plotSub = F, plotText = T, dropIntercept = T,  revOrder = T) # without random effects
```

## Avoid condition
```{r}
tus_avoid <- tus_filtered %>% filter(OutValence == "Avoid")
mcumavoid_full <- lmer(cumulative_reward ~ req_action*condition + (req_action*condition | ID), data  = tus_avoid)
summary (mcumavoid_full) 
```

### check for singularity and effect of random slopes
```{r}
isSingular(mcumavoid_full)

# Diagnosis with RePsychLing approach: PCA on random effects variance-covariance estimates
rePCA_full <- rePCA(mcumavoid_full)
summary(rePCA_full$ID)
```

### fit reduced model
```{r}
mcumavoid <- lmer(cumulative_reward ~ req_action*condition + (req_action + condition | ID), data  = tus_avoid)
summary (mcumavoid) 
tab_model(mcumavoid)
```

### display simple effects for each condition
```{r}
emmeans(mcumavoid, pairwise ~ condition | req_action)
```
### plot effects 
```{r}
plot(allEffects(mcumavoid), ask=FALSE)

```


```{r}

Labels = c("Intercept", "Required Action", "Stimulation AI", "Stimulation dACC", "Req. Action x AI", "Req. Action x dACC")
pavoid <- custom_coefplot(mcumavoid, yLabels = Labels,
                      plotSub = F, plotText = T, dropIntercept = T,  revOrder = T) # without random effects
```