---
title: "GNG_TUS_Study_1_320trials_PROCESSING"
author: "nomi"
date: "2023-10-31"
output: html_document
---

#READ FILE
```{r setup, include=FALSE}
library(readr)
tus <- read_csv("GNG_TUS_S1.csv")
View(tus)
```

 #PROCESSING


## MEAN RT - PRESSES 
```{r}
tus_presses <- subset(tus, RT != "0") # exlude 0s (no presses)
RT_presses <-tus_presses%>%  group_by(condition) %>% 
  summarise(Mean_RT = mean(RT, na.rm = TRUE))
RT_presses_many_variables <-tus_presses %>%  group_by(condition, req_action, correct, response) %>% 
  summarise(Mean_RT = mean(RT, na.rm = TRUE))
```

## MEAN CORRECT
```{r}
correct_res <-tus%>%  group_by(condition, ID) %>% 
  summarise(correct = mean(correct))
RT_presses_many_variables <-tus_presses %>%  group_by(condition, req_action, correct, response) %>% 
  summarise(Mean_RT = mean(RT, na.rm = TRUE))
```

## Distribution of RT
```{r}
tus_presses <- subset(tus, RT != "0") # exlude 0s (no presses)
RT_presses <-tus_presses%>%  group_by(RT, ID) %>% 
  summarise(Mean_RT = mean(RT, na.rm = TRUE));RT_presses #%>%
ggplot(data = RT_presses, 
       aes(x = Mean_RT)) + 
  geom_histogram()+ ggtitle ("Distribution of RT for presses") +theme_APA

#mean RT per participant
MeanRTpersub <- tus %>% filter(response == "press")%>% group_by(Cue, ID, req_action, OutValence,condition) %>% summarise(RT = mean(RT))

yarrr::pirateplot(formula = RT ~ req_action + OutValence + condition,    # DV = reaction time, IV1 = required action, IV2 = outcome valence
                  data = MeanRTpersub,           
                  theme = 2,
                 # main = "Condition",
                  ylab = "Reaction Time (ms)",
                  ylim = c(400, 1000),
                  bean.f.o = .4, # Bean fill
                  bean.b.o = .2, # Light bean border
                  point.o = .5, # Points (opacity)
                  inf.disp = "line",
                  inf.f.o = 0.8, # Inference fill
                  inf.b.o = 0.8, # Inference border
                  avg.line.o = 0, # Average line
                  point.pch = 21,
                  point.bg = "white",
                  point.cex = .7) + theme_APA
```

## Proportion of GO response per condition 
**two participants have 21-22 or 23 trials of a Cue- NOT SURE why?.Also NAs count as over 20 trial, but omitted here.**
```{r}
# compute proportion of go responses for each participant (first sum per ID, then feed that into general summary)
MeanGoResppersub <- tus %>% group_by(ID, Cue, req_action, OutValence, block, TrialCount) %>% summarise(GoResponse = mean(GoResponse))
MeanGoResppersub <- na.omit(MeanGoResppersub)
MeanGoResp <- MeanGoResppersub %>% group_by(Cue, req_action, block, OutValence, TrialCount) %>% summarise(GoResponse = mean(GoResponse))

#plot of p(Go) responses 
ggplot(MeanGoResp) + 
  geom_smooth(aes(TrialCount, GoResponse,colour=OutValence, lty = req_action)) +
  scale_colour_brewer(palette = "Set1") +
  labs(y = "p(GO)", x = "Trial", title = "Trial-by-trial behaviour") +
  xlim (0,20) +theme_bw() 
#plot of p(Go) responses per block
ggplot(MeanGoResp) + 
  geom_smooth(aes(TrialCount,GoResponse,colour=OutValence, lty = req_action)) +
  scale_colour_brewer(palette = "Set1") +
  facet_grid(~block)+
  theme_bw() +
  labs(y = "p(GO)", x = "Trial", title = "Trial-by-trial behaviour") +
  xlim(0, 20)
```


## Session 
### It seems to be significant. In the first session they do worse.
```{r}
# compute proportion of correct responses for each participant
tus_correct_sub <- tus %>% group_by(ID, OutValence,session,  condition, req_action) %>% summarise(correct = mean(correct))
# compute mean proportion of go responses 
tus_correct <- tus_correct_sub %>% group_by(OutValence, session, req_action, condition) %>% summarise(correct = mean(correct))


#plot session

  #re-ordering levels to show as 1,2,3 in the x-axis
tus_correct$session <- factor(tus_correct$session, levels = c("1", "2", "3"))

pirateplot(formula = correct ~ session +condition,
           data = tus_correct,
                           theme = 0,
           #main = "Fully customized pirateplot",
           #pal = "southpark", # southpark color palette
           bean.f.o = .7, # Bean fill
           point.o = .3, # Points
           inf.f.o = .3, # Inference fill
           inf.b.o = .8, # Inference border
           avg.line.o = 1, # Average line
           bar.f.o = .5, # Bar
           inf.f.col = "white", # Inf fill col
           inf.b.col = "black", # Inf border col
           avg.line.col = "black", # avg line col
           #bar.f.col = gray(.8), # bar filling color
           point.pch = 21,
           point.bg = "white",
           point.col = "black",
           point.cex = .7)+theme_APA
         # ylim = c(0.1, 1.0))

#without "condition"
pirateplot(formula = correct ~ session,
           data = tus_correct,
           theme = 0,
           bean.f.o = .7,
           point.o = .3,
           inf.f.o = .3,
           inf.b.o = .8,
           avg.line.o = 1,
           bar.f.o = .5,
           inf.f.col = "white",
           inf.b.col = "black",
           avg.line.col = "black",
           point.pch = 21,
           point.bg = "white",
           point.col = "black",
           point.cex = .7) + theme_APA
```


#proportion of GO response per type of Stimulation (sham, ai, dACC) - NADEIDE  and ELSA to check
```{r}
    #AI - 
ai <- subset(tus, condition == "c.ai")

# compute proportion of go responses for each participant
MeanGoResppersub_ai <- ai %>% group_by(ID, Cue, req_action, OutValence, TrialCount) %>% summarise(GoResponse = mean(GoResponse))

MeanGoResp.ai <- MeanGoResppersub_ai %>% group_by(Cue, req_action, OutValence, TrialCount) %>% summarise(GoResponse = mean(GoResponse))

#plot
ai_rolavg<- ggplot(MeanGoResp.ai) + 
  geom_smooth(aes(TrialCount, GoResponse,colour=OutValence, lty = req_action)) +
  scale_colour_brewer(palette = "Set1") +
  labs(y = "p(GO)", x = "Trial", title = "Trial-by-trial behaviour for AI") +
   xlim(NA, 20)+
 theme_bw() 


    #dACC - 
dacc <- subset(tus, condition == "b.dacc")
#dacc <- na.omit(dacc)

# compute proportion of go responses for each participant
MeanGoResppersub_dacc <- dacc %>% group_by(ID, Cue, req_action, OutValence, TrialCount) %>% summarise(GoResponse = mean(GoResponse))
MeanGoResp.dacc <- MeanGoResppersub_dacc %>% group_by(Cue, req_action, OutValence, TrialCount ) %>% summarise(GoResponse = mean(GoResponse))

#plot
dacc_rolavg<- ggplot(MeanGoResp.dacc) + 
  geom_smooth(aes(TrialCount, GoResponse,colour=OutValence, lty = req_action)) +
  scale_colour_brewer(palette = "Set1") +
  labs(y = "p(GO)", x = "Trial", title = "Trial-by-trial behaviour for dACC")+
   xlim(NA, 20)+ theme_bw() 



    #Sham
sham <- subset(tus, condition == "a.sham")

# compute proportion of go responses for each participant
MeanGoResppersub_sham <- sham %>% group_by(ID, Cue, req_action, OutValence, TrialCount) %>% summarise(GoResponse = mean(GoResponse))

MeanGoResp.sham <- MeanGoResppersub_sham %>% group_by(Cue, req_action, OutValence, TrialCount) %>% summarise(GoResponse = mean(GoResponse))

#plot
sham_rolavg<- ggplot(MeanGoResp.sham) + 
  geom_smooth(aes(TrialCount, GoResponse,colour=OutValence, lty = req_action)) +
  scale_colour_brewer(palette = "Set1") +
  labs(y = "p(GO)", x = "Trial", title = "Trial-by-trial behaviour for sham") +
   xlim(NA, 20)+
 theme_bw() 

#roll avg per CONDITION
rol_avg <- ggarrange(sham_rolavg, ai_rolavg, dacc_rolavg,
                    #labels = c("GW", "GAL", "NGW", "NGL"), 
                  ncol = 2, nrow = 2);rol_avg
```

##rolling average per CUE for all three conditions (plot with NGW for three conditions (sham, ai, dACC), plot GW..etc.)

  ***it looks like stimulation to ACC increases the propensity to press in the Go condition. And STIM to both areas slows down learning in the noGO condition***
```{r}
#Grey area is CI

#GW
GW <- subset(tus, Cue == "GW")

# compute proportion of go responses for each participant
MeanGoResppersub_gw <- GW %>% group_by(ID, req_action, OutValence, TrialCount, condition) %>% summarise(GoResponse = mean(GoResponse))
MeanGoResppersub_gw <- na.omit(MeanGoResppersub_gw)
MeanGoResp_gw <- MeanGoResppersub_gw %>% group_by(req_action, OutValence, TrialCount, condition) %>% summarise(GoResponse = mean(GoResponse))

#plot######################play with lines
GW<-ggplot(data=MeanGoResp_gw, mapping =aes(TrialCount, GoResponse, colour=condition)) + 
  geom_smooth(linetype = "longdash") +
  scale_colour_brewer(palette = "Set1") +
   #facet_grid(~condition)+
   xlim(NA, 20)+
  ylim(0.05, 0.9)+
  labs(y = "p(GO)", x = "Trial", title = "Trial-by-trial behaviour_GW") +theme_bw() 

#GAL
GAL <- subset(tus, Cue == "GAL")

# compute proportion of go responses for each participant
MeanGoResppersub_gal <- GAL %>% group_by(ID, TrialCount, condition) %>% summarise(GoResponse = mean(GoResponse))
MeanGoResppersub_gal <- na.omit(MeanGoResppersub_gal)
MeanGoResp_gal <- MeanGoResppersub_gal %>% group_by(TrialCount, condition) %>% summarise(GoResponse = mean(GoResponse))

#plot
GAL<-ggplot(data=MeanGoResp_gal, mapping =aes(TrialCount, GoResponse, colour=condition)) + 
  geom_smooth(linetype = "longdash") +
  scale_colour_brewer(palette = "Set1") +
   #facet_grid(~condition)+
   xlim(NA, 20)+
     ylim(0.05, 0.9)+
  labs(y = "p(GO)", x = "Trial", title = "Trial-by-trial behaviour_GAL") +theme_bw() 

#NGW
NGW <- subset(tus, Cue == "NGW")

# compute proportion of go responses for each participant
MeanGoResppersub_NGW <- NGW %>% group_by(ID, TrialCount, condition) %>% summarise(GoResponse = mean(GoResponse))
MeanGoResppersub_NGW <- na.omit(MeanGoResppersub_NGW)
MeanGoResp_NGW <- MeanGoResppersub_NGW %>% group_by(TrialCount, condition) %>% summarise(GoResponse = mean(GoResponse))

#plot - need to work on linetype
NGW<-ggplot(MeanGoResp_NGW) + 
  geom_smooth(aes(TrialCount, GoResponse, colour=condition )) +
  scale_colour_brewer(palette = "Set1") +
  # facet_grid(~condition)+
   xlim(NA, 20)+
     ylim(0.05, 0.9)+
  labs(y = "p(GO)", x = "Trial", title = "Trial-by-trial behaviour_NGW") +theme_bw() 



#NGW
NGL <- subset(tus, Cue == "NGL")

# compute proportion of go responses for each participant
MeanGoResppersub_NGL <- NGL %>% group_by(ID, TrialCount, condition) %>% summarise(GoResponse = mean(GoResponse))
MeanGoResppersub_NGL <- na.omit(MeanGoResppersub_NGL)
MeanGoResp_NGL <- MeanGoResppersub_NGL %>% group_by(TrialCount, condition) %>% summarise(GoResponse = mean(GoResponse))

#plot
NGL<-ggplot(MeanGoResp_NGL) + 
  geom_smooth(aes(TrialCount, GoResponse, colour=condition )) +
  scale_colour_brewer(palette = "Set1") +
  # facet_grid(~condition)+
   xlim(NA, 20)+
      ylim(0.05, 0.9)+
  labs(y = "p(GO)", x = "Trial", title = "Trial-by-trial behaviour_NGL") + theme_bw() 



#CUES PER CONDITION
cues <- ggarrange(GW, GAL, NGW, NGL,
                    #labels = c("GW", "GAL", "NGW", "NGL"), 
                  ncol = 2, nrow = 2);cues
   #ylim(0.05, 0.9); 
```


## Probability of correct per participant ***IS THAT CORRECT?***
```{r}
tus_correct<-tus %>%  group_by(ID, OutValence,condition, req_action) %>% summarise(correct = mean(correct))
yarrr::pirateplot(formula = correct ~ condition  +req_action +OutValence,    
                  data = tus_correct,           
                  theme = 2,
                 #main = "Proba_correct/condition",
                  ylab = " (p) of correct",
                  ylim = c(0.1, 1.15),
                  bean.f.o = .4, # Bean fill
                  bean.b.o = .2, # Light bean border
                  point.o = .5, # Points (opacity)
                  inf.disp = "line",
                  inf.f.o = 0.8, # Inference fill
                  inf.b.o = 0.8, # Inference border
                  avg.line.o = 0, # Average line
                  point.pch = 21,
                  point.bg = "white",
                  point.cex = .7)
```

# ACCURACY PLOTS (x6)
### proportion of correct per participant per condition ***IMPORTANT FOR THE GW FOR THE AI***

```{r}
# 1. compute proportion of go responses for each participant <- same as aboe I think
tus_correct_sub <- tus %>% group_by(ID, OutValence, condition, req_action) %>% summarise(correct = mean(correct))
# compute mean proportion of go responses 
tus_correct_meaned <- tus_correct_sub %>% group_by(OutValence, req_action, condition) %>% summarise(correct = mean(correct))


pirateplot(formula = correct ~ condition  + req_action +OutValence,
           data = tus_correct_meaned,
           theme = 1,
           main = "Accuracy",
           bar.f.o = .5, 
           point.o = .5, 
          ylim = c(0.5, 1.0))+theme_APA

# 2.THE SAME AS ABOVE 
pirateplot(formula = correct ~ condition  + OutValence +req_action,
           data = tus_correct_meaned,
                           theme = 0,
           #main = "Fully customized pirateplot",
           #pal = "southpark", # southpark color palette
           bean.f.o = .6, # Bean fill
           point.o = .3, # Points
           inf.f.o = .7, # Inference fill
           inf.b.o = .8, # Inference border
           avg.line.o = 1, # Average line
           bar.f.o = .5, # Bar
           inf.f.col = "white", # Inf fill col
           inf.b.col = "black", # Inf border col
           avg.line.col = "black", # avg line col
           #bar.f.col = gray(.8), # bar filling color
           point.pch = 21,
           point.bg = "white",
           point.col = "black",
           point.cex = .7)+ theme_APA

# 3. same with stat_summary
tus_correct <- na.omit(tus_correct)

tus_acc_plot <-ggplot(data=tus_correct, aes( x=condition, y=correct, fill=condition))+  
  stat_summary(fun.y = mean, geom = "bar") + 
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.3); tus_acc_plot

 tus_acc_plot + facet_grid(req_action ~ OutValence) + theme_APA 


 #TRYING ADDING ERROR BARS AS i CANNOT DO IT WITH THE ABOVE CODE

# 4. Calculate summary statistics (mean and standard deviation)

ppts<-tus %>% group_by(ID) %>%
   distinct(ID) %>% 
  nrow() # number of participants

MeanGoResppersub_cond <- tus %>% group_by(ID, Cue, req_action, OutValence, block, TrialCount, condition, correct) %>% summarise(GoResponse = mean(GoResponse))
MeanGoResppersub_cond <- na.omit(MeanGoResppersub_cond)
#MeanGoResppersub_cond <- MeanGoResppersub_cond %>% group_by(Cue, req_action, block, OutValence, TrialCount) %>% summarise(GoResponse = mean(GoResponse))

summary_data <- MeanGoResppersub_cond %>%
  group_by(condition, req_action, OutValence) %>%
  summarise(
    mean_correct = mean(correct),
    sd_correct = sd(correct),
    count = n(),
    se_correct =sd_correct/sqrt(ppts),
  ) %>%
  na.omit()


# Create a ggplot with error bars, bars, and facets <- i think pirate plot in line 541 better!!!!!
ggplot(summary_data, aes(x = condition, y = mean_correct, ymin = mean_correct - se_correct, ymax = mean_correct + se_correct, fill = condition)) +
  geom_errorbar(position = position_dodge(width = 0.75), width = 0.2) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.75), width = 0.5, alpha = 0.5) +
  geom_text(aes(label = round(mean_correct, 2)), vjust = -0.5, position = position_dodge(width = 0.75)) +
  facet_grid(req_action ~ OutValence) +
  theme_APA




# 5. add points to the above 

# Merge summary_data and tus data
merged_data <- merge(tus, summary_data, by = "condition", all.x = TRUE) #merging should be a left join. In a left join, all rows from the left data frame (tus in this case) will be retained, and matching rows from the right data frame (summary_data) will be added. If there are no matches, the columns from the right data frame will contain missing values (NA).
merged_data <- merged_data %>% na.omit()


# Calculate the minimum and maximum y-values in your data
            #y_min <- min(summary_data$mean_correct - summary_data$se_correct)
            #y_max <- max(summary_data$mean_correct + summary_data$se_correct)

# Create a ggplot with error bars, bars, data points, and facets
ggplot(data = summary_data, aes(x = condition, y = mean_correct, fill = condition)) +
  geom_errorbar(aes(ymin = mean_correct - se_correct, ymax = mean_correct + se_correct),
                position = position_dodge(width = 0.75), width = 0.2) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.75), width = 0.5, alpha = 0.5) +

  # Use merged_data for geom_point instead of tus
  geom_point(data = merged_data, aes(x = condition, y = mean_correct, color = condition),
             position = position_dodge(width = 0.75), size = 1)+
  geom_text(aes(label = round(mean_correct, 3)), vjust = -0.5, position = position_dodge(width = 0.75)) +
  facet_grid(req_action ~ OutValence) +  
  theme_APA +
  # Set y-axis limits dynamically based on data
                #ylim(y_min, y_max)
  coord_cartesian(ylim=c(0.30,1))




# 6. YET ANOTHET PIRATE PLOT
# Filter the data to exclude values outside the desired y-axis range
tus_filtered <- tus_correct %>% filter(correct >= 0.40 & correct <= 1)

#pirate plot
pirateplot(formula = correct ~ condition  + req_action +OutValence,
           data = tus_filtered,
                           theme = 0,
           #main = "Fully customized pirateplot",
           #pal = "southpark", # southpark color palette
           bean.f.o = .6, # Bean fill
           point.o = .3, # Points
           inf.f.o = .7, # Inference fill
           inf.b.o = .8, # Inference border
           avg.line.o = 1, # Average line
           bar.f.o = .5, # Bar
           inf.f.col = "white", # Inf fill col
           inf.b.col = "black", # Inf border col
           avg.line.col = "black", # avg line col
           #bar.f.col = gray(.8), # bar filling color
           point.pch = 21,
           point.bg = "white",
           point.col = "black",
           point.cex = .7)+theme_APA
           #coord_cartesian(ylim=c(0.30,0.9))


```


              ## I THINK I DO NOT NEED THIS CHUNK

#presses for correct  and presses for incorrect (nogos) - ***SEE COMMENTS FOR FURTHER EXPLANATION*** ALSO
         ****IMPORTANT FOR THE GW FOR THE AI****
```{r}
#means - PRESSES FOR GOs (that is pressed when they supposed to be pressing or else pressed for the Go conditions)

presses_for_correct <- subset(tus, response != "no_press"& correct == "1") # that is for both Goes (GW and GAL)
  press_mean_ID<-presses_for_correct %>% group_by(ID, OutValence, condition, req_action) %>% count(correct = "1")%>%summarize (n=mean(n))
  press_mean_cr  <- press_mean_ID %>% group_by(OutValence, condition, req_action)%>%summarize (n=mean(n))
  
pirateplot(formula = n ~ condition  + req_action + OutValence,
           main = "presses for GAL(left) and GW (right)",
             data = press_mean_cr,
           theme = 2,
           bar.f.o = .5,
           ylim = c(0, 80),
                  bean.f.o = .4, # Bean fill
                  bean.b.o = .2, # Light bean border
                  point.o = .5, # Points (opacity)
                  inf.disp = "line",
                  inf.f.o = 0.5, # Inference fill
                  inf.b.o = 0.5, # Inference border
                  avg.line.o = 0, # Average line
                  point.pch = 21,
                  point.bg = "black",
                  point.cex = 1) #For GW, when AI was stimulated. participants pressed 
``` 


## How about RTs? ***NB COULD YOU CHECK PLEASE????***

```{r}

# 1. Calculate summary statistics (mean and standard deviation)

      #filter data to exclude very high values
 filtered_data_rt <- tus %>%filter(RT >= 100, RT <= 1100)

pirateplot(formula = RT ~ condition  + req_action +OutValence,
           data = filtered_data_rt,
                           theme = 0,
           #main = "Fully customized pirateplot",
           #pal = "southpark", # southpark color palette
           bean.f.o = .2, # Bean fill
           point.o = .3, # Points
           inf.f.o = .7, # Inference fill
           inf.b.o = .8, # Inference border
           avg.line.o = 1, # Average line
           bar.f.o = .5, # Bar
           inf.f.col = "white", # Inf fill col
           inf.b.col = "black", # Inf border col
           avg.line.col = "black", # avg line col
           #bar.f.col = gray(.8), # bar filling color
           point.pch = 21,
           point.bg = "white",
           point.col = "black",
           point.cex = .7)+theme_APA


# 2. compute mean_rt for each participant - ?????????not sure if this is OK - i might ignore it
Meanrtpersub_rt <- tus %>% group_by(ID, req_action, OutValence, condition, RT) %>% summarise(mean_rt = mean(RT))
Meanrtpersub_rt <- na.omit(Meanrtpersub_rt)
Meanrtpersub_rt <- Meanrtpersub_rt %>% group_by(req_action, OutValence, condition) %>% summarise(mean_rt = mean(mean_rt))

pirateplot(formula =  mean_rt ~ condition  + req_action +OutValence,
           data = Meanrtpersub_rt,
                           theme = 0,
           main = "mean_RT per subject",
           #pal = "southpark", # southpark color palette
           bean.f.o = .2, # Bean fill
           point.o = .3, # Points
           inf.f.o = .7, # Inference fill
           inf.b.o = .8, # Inference border
           avg.line.o = 1, # Average line
           bar.f.o = .5, # Bar
           inf.f.col = "white", # Inf fill col
           inf.b.col = "black", # Inf border col
           avg.line.col = "black", # avg line col
           #bar.f.col = gray(.8), # bar filling color
           point.pch = 21,
           point.bg = "white",
           point.col = "black",
           point.cex = .7)+theme_APA



#  3. AND with full tus 
Meanrtpersub_rt2 <- tus %>% group_by(ID, Cue, req_action, OutValence, block, TrialCount, condition, RT) %>% summarise(mean_rt = mean(RT))
Meanrtpersub_rt2 <- na.omit(Meanrtpersub_rt2)


summary_data_rt <- Meanrtpersub_rt2 %>%
  group_by(condition, req_action, OutValence) %>%
  summarise(
    mean_rt = mean(RT),
    sd_rt = sd(RT),  # Calculate the standard deviation of RT
    count = n(),
    se_rt = sd_rt / sqrt(ppts)  # Calculate the standard error
  ) %>%
  na.omit()

# Create a ggplot with error bars, bars, and facets - pirate plot in the beginning is better (for RTs) - line 286 
ggplot(summary_data_rt, aes(x = condition, y = mean_rt, ymin = mean_rt - se_rt, ymax = mean_rt + se_rt, fill = condition)) +
  geom_errorbar(position = position_dodge(width = 0.75), width = 0.2) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.75), width = 0.5, alpha = 0.5) +
  geom_text(aes(label = round(mean_rt, 2)), vjust = -0.5, position = position_dodge(width = 0.75)) +
 facet_grid(req_action ~ OutValence) +
theme_APA

 # 4. as above - adding data points
        #Merge summary_data and tus data 
merged_data_rt <- merge(tus, summary_data_rt, by = "condition", all.x = TRUE) 
              #merged_data_rt <- merged_data_rt %>% na.omit()

# Create a ggplot with error bars, bars, data points, and facets
ggplot(data = summary_data_rt, aes(x = condition, y = mean_rt, fill = condition)) +
  geom_errorbar(aes(ymin = mean_rt - se_rt, ymax = mean_rt + se_rt),
                position = position_dodge(width = 0.75), width = 0.2) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.75), width = 0.5, alpha = 0.5) +

  # Use merged_data for geom_point instead of tus
  geom_point(data = merged_data_rt, aes(x = condition, y = mean_rt, color = condition),
             position = position_dodge(width = 0.75), size = 2, alpha = 0.5) +
  geom_text(aes(label = round(mean_rt, 3)), vjust = -0.5, position = position_dodge(width = 0.75)) +
  facet_grid(req_action ~ OutValence) +
  theme_APA
```


## performance per participant
```{r}
#summary - correct Cues
ggplot(tus,
       aes(x=Cue, y= correct, color = Cue, fill= Cue)) + 
  geom_bar(stat = "identity")

#correct counts per Cue
ccc<-tus %>% group_by (Cue)%>% count (correct);View (ccc)

#correct counts per Cue per ID
ccc_id<-tus %>% group_by (Cue, ID)%>% count (correct);View (ccc_id)

#correct per ID
c<-tus %>% filter(correct == "1")%>% group_by (ID)%>% count (correct);c

#response per ID
response_per_ppt <-tus %>% group_by (ID)%>% count (response);View (response_per_ppt)

mean(c$n) #avg of 294 correct responses--> 
          #may be if a person has less than 230 or 210? correct responses --> CUT? or below 53? see below aggregate
```
   

## PROPORTIONs - correct PER PARTCIPANT
```{r}
#the proportion of 1s by participant, + more i.e. sound, and language.
#Because the proportion of 1s in a vector with only 0s and 1s is just the mean, this should work:

df <- aggregate(data=tus, correct ~ ID, FUN="mean")#fun = mean #https://r-coder.com/aggregate-r/
p <- ggplot(df)
p <- p + geom_bar(mapping=aes(x=correct, y=ID), stat='identity')+
  geom_vline(xintercept = 0.53, col = "red")+ 
  geom_vline(xintercept = 0.50, col = "grey")+
   geom_vline(xintercept = 0.80, col = "green")+
  geom_text(aes(x=0.54, label="53%", y=4), colour="black", angle=90) +
geom_text(aes(x=0.49, label="50%", y=9), colour="black", angle=90)+
  geom_text(aes(x=0.79, label="80%", y=6), colour="black", angle=90) 
p + ylab('ID')

#same as above but with stat_summary
ggplot(tus) + 
  stat_summary(aes(x = ID, y = correct), 
               geom = "bar")

#performance per participant and condition
aggregate(data=tus, correct ~ ID+condition, FUN="mean") #fun = mean #https://r-coder.com/aggregate-r/

df_c <- aggregate(data=tus, correct ~ ID +condition, FUN="mean")
 
ggplot(data = df_c) + 
  geom_bar(mapping = aes(fill = condition, x = ID, y = correct), stat = "identity", position = "dodge")

#same but with lines and dots
 df_c %>%ggplot(aes(condition, correct, color=ID)) +
   #geom_boxplot()+
  geom_point(aes(fill=ID),size=5) +
 # scale_x_log10()+
  geom_line(aes(group = ID),color="grey")
#ggsave("#performance per participant and condition.png")


#performance per  condition - awful
aggregate(data=tus, correct ~ condition, FUN="mean") #fun = mean #https://r-coder.com/aggregate-r/

df_con <- aggregate(data=tus, correct ~ condition, FUN="mean")
 
ggplot(data = df_con) + 
  geom_bar(mapping = aes(fill = condition, x = condition, y = correct), stat = "identity", position = "dodge")
```
 
 ## RTs for participants 
```{r}
#rt per participant per condition
aggregate(data=tus, RT ~ ID+condition, FUN="mean") #fun = mean #https://r-coder.com/aggregate-r/

df_rt <- aggregate(data=tus, RT ~ ID +condition, FUN="mean")
 
ggplot(data = df_rt) + 
  geom_bar(mapping = aes(fill = condition, x = ID, y = RT), stat = "identity", position = "dodge") 
  

#same but with lines and dots
  df_rt %>%ggplot(aes(condition, RT, color=ID)) +
   #geom_boxplot()+
  geom_point(aes(fill=ID),size=5) +
 #scale_x_log10()+
  geom_line(aes(group = ID),color="grey")
  
#-------------------------------
  
  #for GW only (correct) - NO POINT
  gwin <- subset(tus, Cue == "GW")

  gwin_cr <- aggregate(data=gwin, correct ~ ID +condition, FUN="mean")

gwin_cr %>%ggplot(aes(condition, correct, color=ID)) +
   #geom_boxplot()+
  geom_point(aes(fill=ID),size=5) +
 #scale_x_log10()+
  geom_line(aes(group = ID),color="grey")


  #for NGW only (RT) - NO POINT

gwin_rt <- aggregate(data=gwin, RT ~ ID +condition, FUN="mean")

gwin_rt %>%ggplot(aes(condition, RT, color=ID)) +
   #geom_boxplot()+
  geom_point(aes(fill=ID),size=5) +
 #scale_x_log10()+
  geom_line(aes(group = ID),color="grey")
```


