---
title: "GNG_TUS_Study_1_320trials_preprocessing"
author: "nomi"
date: "2023-10-31"
output: html_document
---

 

# LOAD LIBRARIES
```{r}
#library(Rccp)
#library(rlang)
library(tibbletime)
library(purrr)
library(stringr)
library(report)
#library(ggplot)
library(ggplot2)
library(dplyr)
#library(lmer)
library(tidyverse)
library(patchwork)
library(ggpubr)
library(jtools) #for explanation of lmer
library(yarr)
library (yarrr)
library(afex)
#install.packages("devtools")
#devtools::install_github("mikabr/ggpirate")
#library(ggpirate)
#p_load ( rms, htmltools, bridgesampling, rstanarm, magrittr, scales, RColorBrewer, 
# parsnip, zoo, wesanderson, yarr, BiocManager, afex, GGally, lmerTest, aod, splines)
```



    #PREPROCESSING

## insert .txt files
```{r}
a.sham<- tibble(filename = list.files("1.SHAM", "*.txt", full.names=TRUE)) %>% 
    group_by(filename) %>% 
    do(read.table(.$filename))
c.ai<- tibble(filename = list.files("3.AI", "*.txt", full.names=TRUE)) %>% 
    group_by(filename) %>% 
    do(read.table(.$filename))
b.dacc<- tibble(filename = list.files("2.dACC", "*.txt", full.names=TRUE)) %>% 
    group_by(filename) %>% 
    do(read.table(.$filename))
```

## add condition column
```{r}
a.sham <- a.sham %>%
      mutate (condition="a.sham")
c.ai <- c.ai %>%
      mutate (condition="c.ai")
b.dacc <- b.dacc %>%
      mutate (condition="b.dacc")
```

## Set variable names
```{r}
a.sham <- a.sham %>% set_names(c("ID", "stim_ID", "GW", "GAL", "NGW", "NGL", "jitter1", 
              "jitter2", "RT", "outcomefeed", "condition"))
b.dacc <- b.dacc %>% set_names(c("ID", "stim_ID", "GW", "GAL", "NGW", "NGL", "jitter1", 
              "jitter2", "RT", "outcomefeed", "condition"))
c.ai <- c.ai %>% set_names(c("ID", "stim_ID", "GW", "GAL", "NGW", "NGL", "jitter1", 
              "jitter2", "RT", "outcomefeed", "condition"))
```


## combine datasets
```{r}
tus <-bind_rows(a.sham, c.ai, b.dacc)

```


## add session column
```{r}
# Extract numbers at the end of each level and create a new column
tus<-tus %>%
  mutate(session = as.factor(str_extract(ID,"(?<=\\D)\\d+(?=_log.txt)")))
#View(tus)
```


## Change name of ID rows to match the subj_ID (i.e.  "pilot data/DBGE0324_log.txt" --> "DBGE0324")
```{r}
tus <- tus %>%
      mutate_at("ID", str_replace, "1.SHAM/", "")# & "log.txt", "")
tus <- tus %>%
      mutate_at("ID", str_replace, "3.AI/", "")
tus <- tus %>%
      mutate_at("ID", str_replace, "2.dACC/", "")
tus <- tus %>%
      mutate_at("ID", str_replace, "_SHAM_2", "")
tus <- tus %>%
      mutate_at("ID", str_replace, "_SHAM_3", "")
tus <- tus %>%
      mutate_at("ID", str_replace, "_SHAM_1", "")
#tus <- tus %>%
   #   mutate_at("ID", str_replace, "_SHAM__1", "_sham")
tus <- tus %>%
      mutate_at("ID", str_replace, "_dACC_2", "")
tus <- tus %>%
      mutate_at("ID", str_replace, "_dACC_3", "")
tus <- tus %>%
      mutate_at("ID", str_replace, "_dACC_1", "")
#tus <- tus %>%
    #  mutate_at("ID", str_replace, "_ACC_2", "_dACC")
#tus <- tus %>%
#      mutate_at("ID", str_replace, "_ACC_1", "_dACC")
tus <- tus %>%
      mutate_at("ID", str_replace, "_AI_2", "")
tus <- tus %>%
      mutate_at("ID", str_replace, "_AI_3", "")
tus <- tus %>%
      mutate_at("ID", str_replace, "_AI_1", "")
tus <- tus %>%
      mutate_at("ID", str_replace, "_log.txt", "")
#tus <- tus %>%
  #    mutate_at("ID", str_replace, "SINB_0180", "SINB0180")
#copied
#tus <- tus %>%
   #   mutate_at("ID", str_replace, "_Copy", "")


# Rename ID
tus <- tus %>%
  mutate(ID = ifelse(ID == "SSCH0384", "SSCF0384", ID))

```

## Add response col (press - no_press)
```{r}
tus$response <- with(tus, ifelse(RT>0, "press", "no_press"))
tus$GoResponse <- with(tus, ifelse(RT>0, 1, 0)) 
```

## Add Cue column (if stim_ID=NGW then NGW, etc. for  NGL, GW, GAL)
```{r}
tus$Cue <- ifelse(tus$stim_ID == tus$NGL, 'NGL',
                ifelse(tus$stim_ID == tus$NGW, 'NGW', 
                ifelse(tus$stim_ID == tus$GW, 'GW', 
              ifelse(tus$stim_ID == tus$GAL, 'GAL', NA))))
    ```

## Add GNG col (Go-noGO)
```{r}
tus$req_action <- ifelse(tus$stim_ID == tus$NGL, 'noGo',
                ifelse(tus$stim_ID == tus$NGW, 'noGo', 'Go'))   
#NB's way: 
#pilot$ReqAction <- ifelse(pilot$Cue == 'NGL', 'NoGo',
            #       ifelse(pilot$Cue == 'NGW', 'NoGo',
             #      ifelse(pilot$Cue == 'GW', 'Go',
              #      felse(pilot$Cue == 'GAL', 'Go', NA))))

```
 
## Add correct column (0-1)  
```{r}
tus <- tus %>%
  mutate(correct = ifelse(req_action == "noGo", ifelse(response == "no_press", 1, 0), 
         
                    ifelse(req_action == "Go", ifelse(response == "press", 1, 0), 1)))
```
        
## Trial column 
```{r}
#1,2,3...100...320
tus <- tus %>%
  group_by(ID, condition) %>%
  mutate(trial_number = row_number())
```


## block colums 1, 2, 3, 4   =====sos with the trials that have 400 instead of 320
```{r}
tus$block <- ifelse(tus$trial_number == 1:80, '1',
                ifelse(tus$trial_number == 81:160, '2', 
                ifelse(tus$trial_number == 161:240, '3', 
              ifelse(tus$trial_number == 241:320, '4', NA))))
# counts trials of the same condition within each block
count_trials <- rollify(function(x) sum(last(x) == x), window=80)#turns a function 
#into a rolling version of itself for use inside of a call to dplyr::mutate() ,
# however it works equally as well when called from purrr::map()
```

## trial_count column
```{r}
tus <- tus %>%
  group_by(ID, block, condition) %>%
  mutate(TrialCount = count_trials(Cue)) %>%
  group_by(ID, block,condition, Cue) %>%
  mutate(TrialCount = ifelse(is.na(TrialCount), row_number(ID), TrialCount))
```


## Add win_lose column (win - lose) 
```{r}
tus$feedback <- recode_factor(tus$outcomefeed, "-1" = "lose", 
                                "1" = "win", "0"= "neutral")

```
      
## Add Win/Avoid condition column (if stim_ID=NGW then NGW, etc. for  NGL, GW, GAL)
```{r}
tus$OutValence <- ifelse(tus$Cue == 'NGL', 'Avoid',
                   ifelse(tus$Cue == 'NGW', 'Win',
                   ifelse(tus$Cue == 'GW', 'Win',
                   ifelse(tus$Cue == 'GAL', 'Avoid', NA))))
```

## Add salient feedback column only
```{r}
tus <- tus %>%
  mutate(salient = ifelse(feedback == "win","win",
                      ifelse(feedback == "lose", "lose", NA)))
```
    
        #'followup_beha' showing response after feedback + 1 in trial_number
#behaviour after loss and after winning feedback general (followup_beha, followup_beha_binary) 

Explained: Columns 
1. a "followup_beha" column based on feedback showing what response/behaviour they have chosen, go or noGo (press or no_press) after general feedback, neutral, loss, win). 
2. a "followup_beha_binary" column that recodes the followup_beha column as binary (0 for "no_press" and 1 for "press")
```{r}

# Convert feedback column to a factor (if it's not already a factor)
tus$feedback <- as.factor(tus$feedback)

# Mutate column 'followup_beha' showing response after feedback + 1 in trial_number
tus <- tus %>%
  group_by(ID, condition, Cue, req_action) %>%
  mutate(followup_beha = lead(response, order_by = trial_number, default = NA))

# Count the number of occurrences for each level of the Cue column, to check is balanced
 cue_counts <- table(tus$Cue);print(cue_counts)
 
 
# Recode followup_beha as binary (0 for "no_press" and 1 for "press")
tus$followup_beha_binary <- as.numeric(tus$followup_beha == "press")

# Check the recoded variable
table(tus$followup_beha_binary)
```


              # whether they are correct after a correct feedback
              Find the follow up behaviour after receiving the correct feedback (or whether they were correct after receiving the correct feedback 80% and not the 20%)

Explained:
1. "correct_feedback" column
  when NGL and response:no_press and  feedback neutral, then 1 else 0 =>  add to column -> correct_feedback 
  when GW and response: press and and feedback win, then 1, else 0 =>  add to column -> correct_feedback
  when GAL and response press and and feedback neutral, then 1, else 0=>  add tocolumn ->correct_feedback
  when NGW and response no_press and feedback  win, then 1, else 0 =>  add to column ->correct_feedback
  how to find the follow-up behaviour. Create a column called correct_proba_feed
  
  
following correct action (whether they were correct after receiving the correct feedback 80% and not the 20%)
!!!!!!!!!!!!!!!!!! NEUTRAL is ALSO correct when NGL and GAL and they get 0 and feedback was 0

2. "followup_correctfeed" behaviour column, is followup_response after correct feedback (press, no_press, wrong_feed_20%) 

3. "followup_wrong_feed" behaviour column, is what they did after received the unexpected wrong feedback (20%) 

4. "followup_correctfeed_trinary"column is the "followup_correctfeed" coded trinary; (0 for "no_press", 1 for "press", 2 for "wrong_feed_20%). Not sure if of any use.
  
```{r}
# Step 1: Calculate correct_feedback based on specified conditions (check in which instance feedback was correct 80%) - all good!
tus <- tus %>%
  mutate(correct_feedback = case_when(
    is.na(Cue) ~ NA_real_,  # If Cue is NA, assign NA to correct_feedback
    Cue == "NGL" & response == "no_press" & feedback == "neutral" ~ 1,
    Cue == "GW" & response == "press" & feedback == "win" ~ 1,
    Cue == "GAL" & response == "press" & feedback == "neutral" ~ 1,
    Cue == "NGW"  & response == "no_press"& feedback == "win" ~ 1,
    Cue == "NGL" & response == "press" & feedback == "lose" ~ 1,
    Cue == "GW" & response == "no_press" & feedback == "neutral" ~ 1,
    Cue == "GAL" & response == "no_press" & feedback == "lose" ~ 1,
    Cue == "NGW"  & response == "press"& feedback == "neutral" ~ 1,
    TRUE ~ 0
  ))

        #check percentages and if 80% 20%
        table(tus$feedback)
        table(tus$correct_feedback)

                    
total_count <- 28500
count_0s <- 5365
count_1s <- 23153
count_lose <- 4254
count_win <- 9328
count_nutral <- 14918

      # Calculate proportions 
          count_0s <- count_0s / total_count; print(count_0s)
                count_1s <- count_1s / total_count; print (count_1s)

        # Step 2: Calculate followup_response after correct feedback   -called:followup_correctfeed
      # Add a column indicating follow-up response after correct feedback but also indicate response after wrong_feedback_20%

tus <- tus %>%
  mutate(followup_correctfeed = case_when(
    correct_feedback == 1 ~ lead(response, order_by = trial_number, default = "wrong_feed_20%"),
    TRUE ~ "wrong_feed_20%"  # For rows where correct_feedback is not 1, set followup_response as "wrong_feed_20%" (20% where wrong feedback is given - opposite than expected)
  ))

    #Add column to show what behaviour/action they followed after wrong feedback is given
tus <- tus %>%
  mutate(followup_wrong_feed = case_when(
    correct_feedback == 0 ~ lead(response, order_by = trial_number, default = "correct_feedback"),
    TRUE ~ "correct_feedback"
  ))


# Calculate the percentage of instances of "wrong_feed_20%" in followup_correctfeed column
wrong_feedback_percentage <- mean(tus$followup_correctfeed == "wrong_feed_20%") * 100
wrong_feedback_percentage # 20.69 ! perfect


# Recode followup_correctfeed as trinary (0 for "no_press", 1 for "press", 2 for "wrong_feed_20%")
tus$followup_correctfeed_trinary <- ifelse(tus$followup_correctfeed == "press", 1,
                                           ifelse(tus$followup_correctfeed == "no_press", 0, 2))

# Check the recoded variable
table(tus$followup_correctfeed_trinary)


```

         
         
          #Actual reward, excluding wrong feedback (20%) column - called: actual_reward
         
         
  "actual_reward" column
  
  FOR GW & NGW: correctfeedback == 1 & feedback == win & correct ==1 then "reward"
  FOR GW & NGW: correctfeedback == 1 & feedback == neutral & correct ==0 then "no_reward"
  FOR NGL & GAL: correctfeedback == 1 & feedback == lose & correct ==0 then "punishment"
  FOR NGL & GAL: correctfeedback == 1 & feedback == neutral & correct ==1 then "no_punishment"
          
          #Reward in general column - called: reward
  
  "reward" column      
  
  Valence == Win & feedback == win, then "reward"
  Valence == Win & feedback == neutral, then "no_reward"          
  Valence == lose & feedback == neutral, then "no_punishment"
  Valence == lose & feedback == lose, then "punishment"

          
```{r}
# actual_reward 
tus$actual_reward <- NA  # Initialize the column with NA values (not counting the wrong_feed_20%)

# Define conditions for actual_reward column
tus$actual_reward[tus$Cue %in% c("GW", "NGW") & tus$correct_feedback == 1 & tus$feedback == "win" & tus$correct == 1] <- "reward"
tus$actual_reward[tus$Cue %in% c("GW", "NGW") & tus$correct_feedback == 1 & tus$feedback == "neutral" & tus$correct == 0] <- "no_reward"
tus$actual_reward[tus$Cue %in% c("NGL", "GAL") & tus$correct_feedback == 1 & tus$feedback == "lose" & tus$correct == 0] <- "punishment"
tus$actual_reward[tus$Cue %in% c("NGL", "GAL") & tus$correct_feedback == 1 & tus$feedback == "neutral" & tus$correct == 1] <- "no_punishment"

# reward 
tus$reward <- NA  # Initialize the column with NA values (not needed I think as all belong in one of four conditions below)

# Define conditions for reward column
tus$reward[tus$OutValence == "Win" & tus$feedback == "win"] <- "reward"
tus$reward[tus$OutValence == "Win" & tus$feedback == "neutral"] <- "no_reward"
tus$reward[tus$OutValence == "Avoid" & tus$feedback == "neutral"] <- "no_punishment"
tus$reward[tus$OutValence == "Avoid" & tus$feedback == "lose"] <- "punishment"

```
          
          #behaviour following reward
          
  "followup_beha_reward" column. Behaviour after general/raw reward
          
```{r}
# Mutate column 'followup_beha_reward' showing response after reward based on groupings
tus <- tus %>%
  group_by(ID, condition, Cue, req_action, reward) %>%
  mutate(followup_beha_reward = lead(response, order_by = trial_number + 1, default = NA))

```
          
     #4 columns added response before followup_beha  before followu_beha_reward and their binary equivalent 
      
           # for the follow_up beha something is going on with the neutral feedback for the ai. In general they are pressing more.
```{r}
# 'followup_beha' and 'followup_beha_reward' need to be factors
# Create binary column for previous response before followup_beha
tus_filtered <- tus_filtered %>%
  group_by(ID, condition, Cue, req_action) %>%
  mutate(
    previous_beha = lag(followup_beha, order_by = trial_number, default = NA),
    previous_beha_binary = as.numeric(previous_beha == "press")  # Binary column
  )

# Create binary column for previous response before followup_beha_reward
tus_filtered <- tus_filtered %>%
  group_by(ID, condition, Cue, req_action) %>%
  mutate(
    previous_beha_reward = lag(followup_beha_reward, order_by = trial_number, default = NA),
    previous_beha_reward_binary = as.numeric(previous_beha_reward == "press")  # Binary column
  )

# Check the recoded variables (binary columns)
table(tus_filtered$previous_beha_binary)
table(tus_filtered$previous_beha_reward_binary)

# Print head of the dataframe to verify
head(tus_filtered[, c("response", "followup_beha", "previous_beha", "previous_beha_binary", "followup_beha_reward", "previous_beha_reward", "previous_beha_reward_binary")])
```




          RT_min column - replacing 0s to 0.001
```{r}
tus <- tus %>%
  mutate(RT_min = ifelse(RT == 0, 0.001, RT))

tus_play <- tus 
```

          
          # IES (nverse Efficiency Score) for Studying Speed-Accuracy Performance
            - the lowest the IES the better the performance

Formula:
IES = RT/1 - PE (proportion of errors) OR
IES = RT/PC (proportion of correct responses)

1. so I need to find the proportion of correct responses first per participant, Cue, condition
2. calculate their IES
3. summarize per condition and Cue maybe? 


          
          # not sure whether IES calculation is correct - problem with the WIN cues as by default have low or 0 proportion of errors. 
          Especially aIns even if less accuracy in GW they were pressing fast, so it turns out to have a better IES score than the other conditions.
  
  #A. Calculate the IES for each row:
```{r}
# Calculate proportion of correct responses
tus$correct_proportion <- tus$correct / 100  #  correct is given as a percentage

# Calculate IES
tus$IES <- tus$RT_min / (1 - tus$correct_proportion)

# Selectively show columns
tus[, (ncol(tus) - 5):(ncol(tus))]

# Summarize by condition
IES_by_cond_cue_id<- tus %>%
  group_by(ID, condition, Cue) %>%
  summarise(
    mean_IES = mean(IES, na.rm = TRUE),  # Calculate the mean IES for each condition
    sd_IES = sd(IES, na.rm = TRUE),  # Calculate the standard deviation of the IES for each condition
    n = n()  # Count the number of observations for each condition
  )

IES_by_cond_cue<- IES_by_cond_cue_id %>%
  group_by(condition, Cue) %>%
  summarise(
    mean_IES = mean(mean_IES, na.rm = TRUE),  # Calculate the mean IES for each condition
    sd_IES = sd(sd_IES, na.rm = TRUE),  # Calculate the standard deviation of the IES for each condition
    n = n()  # Count the number of observations for each condition
  )

print(IES_by_cond_cue) #done by ID first - this one is good


#or
# Step 3: Summarize IES per condition and cue
summary <- tus %>%
  group_by(condition, Cue) %>%
  summarize(mean_IES = mean(IES, na.rm = TRUE))

```
 
 

      #EXCLUSIONS AND SUBSETS

#Exlusion 3SDs still 32 participants
#Exclude 3SDs per condition
#Excluding 4th block for JAKA0154 DACC, SSHHW0093 DACC, SINB0180 AI and SKKY0189 because it contains NAs
#Exclude any trials that Cue presented >20
#Exclude RTs<200ms (only a few 4,5 instances)
# decide what else


Columns:

1. "mean_accuracy" column per participant
2. "excluded" column to show whether included or excluded
```{r}
# Calculate mean accuracy per participant
mean_accuracy_per_participant <- tus %>%
  group_by(ID) %>%
  summarise(mean_accuracy = mean(correct, na.rm = TRUE))

# Calculate mean and standard deviation of mean accuracy
mean_accuracy <- mean(mean_accuracy_per_participant$mean_accuracy)
sd_accuracy <- sd(mean_accuracy_per_participant$mean_accuracy)

# Define lower and upper bounds
lower_bound <- mean_accuracy - 3 * sd_accuracy
upper_bound <- mean_accuracy + 3 * sd_accuracy

# Identify excluded participants
excluded_participants <- mean_accuracy_per_participant %>%
  filter(mean_accuracy < lower_bound | mean_accuracy > upper_bound)

# Add a column to indicate exclusion
mean_accuracy_per_participant <- mean_accuracy_per_participant %>%
  mutate(excluded = ifelse(ID %in% excluded_participants$ID, "Excluded", "Included"))

# Merge exclusion information back into tus dataset
tus <- left_join(tus, mean_accuracy_per_participant, by = "ID"); View(tus)

# Print number of participants before and after exclusion
num_participants_before <- nrow(mean_accuracy_per_participant)
num_participants_after <- num_participants_before - nrow(excluded_participants)

cat("Number of participants before exclusion:", num_participants_before, "\n")
cat("Number of participants after exclusion:", num_participants_after, "\n")


```

      # Exclusion 3sd per condition and ID (none)

new data set "tus_filtered"

Columns added:
1. "mean_correct"  (per condition this time)
2. "sd_correct"    (per condition this time)

```{r}
# Calculate mean and standard deviation for each condition
condition_stats <- tus %>%
  group_by(condition) %>%
  summarise(
    mean_correct = mean(correct, na.rm = TRUE),
    sd_correct = sd(correct, na.rm = TRUE)
  )

# Print the mean and standard deviation for each condition
cat("Mean and Standard Deviation for each condition:\n")
print(condition_stats)

# Join the statistics back to the original data
tus <- tus %>%
  left_join(condition_stats, by = "condition")

# Calculate the mean accuracy for each ID and condition
id_condition_stats <- tus %>%
  group_by(ID, condition) %>%
  summarise(mean_correct_per_id = mean(correct, na.rm = TRUE), .groups = 'drop')

# Join the ID-condition stats back to the statistics
id_condition_stats <- id_condition_stats %>%
  left_join(condition_stats, by = "condition")

# Identify IDs that fall outside the ±3 SD range for any condition
excluded_ids <- id_condition_stats %>%
  filter(mean_correct_per_id < (mean_correct - 3 * sd_correct) |
         mean_correct_per_id > (mean_correct + 3 * sd_correct)) %>%
  distinct(ID)

# Filter out excluded IDs from the original data
tus_filtered <- tus %>%
  filter(!(ID %in% excluded_ids$ID))

# Print number of participants before and after exclusion per condition
num_before_condition <- tus %>%
  distinct(ID, condition) %>%
  group_by(condition) %>%
  summarise(num_participants = n(), .groups = 'drop')

num_after_condition <- tus_filtered %>%
  distinct(ID, condition) %>%
  group_by(condition) %>%
  summarise(num_participants = n(), .groups = 'drop')

cat("Number of participants before exclusion per condition:\n")
print(num_before_condition)

cat("\nNumber of participants after exclusion per condition:\n")
print(num_after_condition)

# Print conditions per ID before exclusion
conditions_per_ID_before <- tus %>%
  filter(!is.na(correct)) %>%
  distinct(ID, condition) %>%
  arrange(ID)  # Sort by ID for clarity

cat("\nConditions per ID before exclusion:\n")
print(conditions_per_ID_before)

# Print conditions per ID after exclusion
conditions_per_ID_after <- tus_filtered %>%
  distinct(ID, condition) %>%
  arrange(ID)  # Sort by ID for clarity

cat("\nConditions per ID after exclusion:\n")
print(conditions_per_ID_after)

# Count conditions per ID before exclusion
conditions_count_before <- tus %>%
  filter(!is.na(correct)) %>%
  group_by(ID) %>%
  summarise(num_conditions = n_distinct(condition), .groups = 'drop') %>%
  arrange(ID)  # Sort by ID for clarity

cat("\nConditions count per ID before exclusion:\n")
#View(conditions_count_before)

# Count conditions per ID after exclusion
conditions_count_after <- tus_filtered %>%
  group_by(ID) %>%
  summarise(num_conditions = n_distinct(condition), .groups = 'drop') %>%
  arrange(ID)  # Sort by ID for clarity

cat("\nConditions count per ID after exclusion:\n")
#View(conditions_count_after)
```



      #deleting 4th block for JAKA0154 DACC, SSHHW0093 DACC, SINB0180 AI and SKKY0189 because it contains NAs
      
```{r}
# Exclude specified rows
tus_filtered <- tus_filtered %>%
  filter(!(block == 4 & ID == "JAKA0154" & condition == "b.dacc")) %>%
  filter(!(block == 4 & ID == "SSHW0093" & condition == "b.dacc")) %>%
  filter(!(block == 4 & ID == "SINB0180" & condition == "c.ai"))%>%
  filter(!(block == 4 & ID == "SKKY0189" & condition == "b.dacc")) %>%
  filter(!(block == 4 & ID == "SKKY0189" & condition == "c.ai"))
```


    # exclude any trials that Cue presented >20
```{r}
tus_filtered<-tus_filtered %>%
 filter(!( ID == "EEMR0429" & condition == "b.dacc")) %>%
 filter(!(ID == "EEMR0429" & condition == "a.sham")) %>%
 filter(!(ID =="SINB0180" & condition == "c.ai"))


# Filter out the rows where TrialCount is greater than 20
tus_filtered <- tus_filtered %>%
  group_by(ID, condition, block, Cue) %>%
  filter(TrialCount <= 20) %>%
  ungroup()
```



   #exclude RTs below 200ms
   
```{r}
tus_filtered <- tus_filtered %>%
  filter(!(RT <= 200 & response == "press"))
```

   
   
   
   
#view conditions by cue per id
```{r}

# Create the table
tus_table <- table(tus_filtered$ID, tus_filtered$stim_ID, tus_filtered$condition)

# Print all matrices
for (cond in dimnames(tus_table)[[3]]) {
  cat("Condition:", cond, "\n")
  print(tus_table[, , cond])
  cat("\n")  # Add a newline for better readability
}
```


    #check presses GW always pressed and NGW never pressed or the opposite to exclude outliers. 
      Data seems OK. A 2nd pair of eyes is needed. 
```{r}
# Calculate the number of presses for each cue per ID
presses_per_cue <- tus_filtered %>%
  group_by(ID, Cue, condition) %>%
  summarize(num_presses = sum(response == "press"))

#View(presses_per_cue)
```



 ##write.csv
```{r}
#data set with no exclusions
write.csv(tus, "GNG_TUS_S1.csv")

#working on this one at the moment - some exclusions, see comment next to it
write.csv(tus_filtered, "GNG_tus_filtered_S1.csv") # excluded: 4blocks with inconsistencies for some and any trials that cue is presented over 20 times per block, also RTs<200ms

```

#exclude accuracy around chance 50% - need to decide!!!
```{r}
# Calculate mean accuracy per ID per condition
    #mean_accuracy_data <- tus_filtered_valid %>%
    #group_by(ID, condition) %>%
    #summarize(mean_accuracy = mean(correct, na.rm = TRUE))

# Identify IDs and conditions that have mean accuracy below 55%
    #excluded_ids_conditions <- mean_accuracy_data %>%
    #filter(mean_accuracy < 0.50) 
# Filter the original dataset to exclude IDs and conditions with mean accuracy below 55%
    #tus_filtered_ex <- tus_filtered_valid %>%
    #anti_join(excluded_ids_conditions, by = c("ID", "condition"))

#View(tus_filtered_ex)


#write.csv(tus_filtered_ex, "tus_filtered_ex.csv")
```

#exclude score point very low  
```{r}
#tus_clean_allexs<-tus_filtered_valid %>%
# filter(!( ID == "JAKA0154" & condition == "c.ai")) %>% #low score
#  filter(!(ID == "KTGO2025" & condition == "b.dacc")) %>% #low score
# filter(!( ID == "ZHHS0560" & condition == "c.ai")) %>%
#   filter(!( ID == "ZHHS0560" & condition == "a.sham")) %>%
#filter(!( ID == "TRWL0072" & condition == "a.sham")) %>%
 # filter(!( ID == "TRWL0072" & condition == "b.dacc")) 
```

